---
title: "Check read counts in binned genome"
author: "Briana Mittleman"
date: 2017-11-30
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->


###Bash script


Split genome into 200bp windows and run the coverage command: 

/project2/gilad/briana/Net-seq/genome_bed/hg19_200bp_window.bed 

/project2/gilad/briana/Net-seq/ref_genes/windows_200


make window_200_cov.sh  



```{bash,eval=FALSE}
#!/bin/bash

#SBATCH --job-name=window_200_cov
#SBATCH --time=8:00:00
#SBATCH --partition=broadwl
#SBATCH --mem=50G
#SBATCH --tasks-per-node=4
#SBATCH --mail-type=END



bedtools coverage -counts -a /project2/gilad/briana/Net-seq/genome_bed/hg19_200bp_window.bed -b /project2/gilad/briana/Net-seq/Net-seq1/data/bed_sort/net1_18486_dep_chr_sort.bed  > /project2/gilad/briana/Net-seq/ref_genes/windows_200/window_200_cov_18486.txt


bedtools coverage -counts -a /project2/gilad/briana/Net-seq/genome_bed/hg19_200bp_window.bed -b /project2/gilad/briana/Net-seq/Net-seq1/data/bed_sort/net1_18508_dep_chr_sort.bed  > /project2/gilad/briana/Net-seq/ref_genes/windows_200/window_200_cov_18508_dep.txt

bedtools coverage -counts -a /project2/gilad/briana/Net-seq/genome_bed/hg19_200bp_window.bed -b /project2/gilad/briana/Net-seq/Net-seq1/data/bed_sort/net1_18508_nondep_chr_sort.bed   > /project2/gilad/briana/Net-seq/ref_genes/windows_200/window_200_cov_18508_nondep.txt

bedtools coverage -counts -a /project2/gilad/briana/Net-seq/genome_bed/hg19_200bp_window.bed -b /project2/gilad/briana/Net-seq/Net-seq1/data/bed_sort/net1_19238_dep_chr_sort.bed   > /project2/gilad/briana/Net-seq/ref_genes/windows_200/window_200_cov_19238.txt

bedtools coverage -counts -a /project2/gilad/briana/Net-seq/genome_bed/hg19_200bp_window.bed  -b /project2/gilad/briana/Net-seq/data/bed_sort/mayer_SRR1575922_chr_sort.bed   > /project2/gilad/briana/Net-seq/ref_genes/windows_200/window_200_cov_mayer.txt 


#bedtools coverage -counts -a /project2/gilad/briana/Net-seq/genome_bed/hg19_200bp_window.bed   -b /project2/gilad/briana/Net-seq/Net-seq1/data/bed/merged_Net1.chr.bed   > /project2/gilad/briana/Net-seq/ref_genes/windows_200/window_200_cov_merged.txt
#step memory exceeded!
```


###Import data  
```{r}
window_200_18486=read.csv("../data/windows_200/window_200_cov_18486.txt", header=FALSE, sep="\t")
window_200_18508_dep=read.csv("../data/windows_200/window_200_cov_18508_dep.txt", header=FALSE, sep="\t")
window_200_18508_nondep=read.csv("../data/windows_200/window_200_cov_18508_nondep.txt", header=FALSE, sep="\t")
window_200_19238=read.csv("../data/windows_200/window_200_cov_19238.txt", header=FALSE, sep="\t")
window_200_mayer= read.csv("../data/windows_200/window_200_cov_mayer.txt", header=FALSE, sep="\t")
```

Add col labels to each file:  
```{r}
colnames(window_200_18486) = c("chr", "start", "end", "count")
colnames(window_200_18508_dep) = c("chr", "start", "end", "count")
colnames(window_200_18508_nondep) = c("chr", "start", "end", "count")
colnames(window_200_19238) = c("chr", "start", "end", "count")
colnames(window_200_mayer) = c("chr", "start", "end", "count")
```


###Plot data 

Data I want to look at: 

* summary per library  


```{r}
summary(window_200_18486$count)
summary(window_200_18508_dep$count)
summary(window_200_18508_nondep$count)
summary(window_200_19238$count)
summary(window_200_mayer$count)
```

Use a plot to see the distribution:  


* summaries not including zero 


Make dataframe excluding the zeros: 
```{r}
window_200_18486_non0= window_200_18486[window_200_18486$count!=0,]
window_200_18508_dep_non0= window_200_18508_dep[window_200_18508_dep$count!=0,]
window_200_18508_nondep_non0= window_200_18508_nondep[window_200_18508_nondep$count!=0,]
window_200_19238_non0= window_200_19238[window_200_19238$count!=0,]
window_200_mayer_non0= window_200_mayer[window_200_mayer$count!=0,]
```

summarise

```{r}
summary(window_200_18486_non0$count)
summary(window_200_18508_dep_non0$count)
summary(window_200_18508_nondep_non0$count)
summary(window_200_19238_non0$count)
summary(window_200_mayer_non0$count)
```



```{r}
plot(sort(log(window_200_19238_non0$count), decreasing=TRUE))
```


* number of entries that are non zero  

```{r}
x= nrow(window_200_18486)
barplot(c(nrow(window_200_18486_non0)/x,nrow(window_200_18508_dep_non0)/x,nrow(window_200_18508_nondep_non0)/x, nrow(window_200_19238_non0)/x), main="Proportion of detected bins", names=c("18486", "18508 \n dep", "18508 \n nondep", "19238"))

nrow(window_200_mayer_non0)/x

```

###Integrate sets:

```{r}
window_non_0_all= nrow(window_200_18486[window_200_18486$count!=0 | window_200_18508_dep$count!=0 | window_200_18486$count!=0,] )
prop_window_non0= window_non_0_all/x
prop_window_non0
```

```{r}
window_non_0_2= nrow(window_200_18486[window_200_18486$count!=0 | window_200_18508_dep$count!=0,] )
prop_window_non0_2= window_non_0_2/x
prop_window_non0_2
```


```{r}
window_non_0_2b= nrow(window_200_18486[window_200_18486$count!=0 |window_200_18486$count!=0,] )
prop_window_non0_2b= window_non_0_2b/x
prop_window_non0_2b
```

###Explore bin overlap

I will combine the depleted samples counts in one data frame:  

```{r}
window_200_3lib= cbind(window_200_18486, window_200_18508_dep$count, window_200_19238$count)
colnames(window_200_3lib)= c("chr", "start", "end", "18486", "18508", "19238")
```

Make a vector with how many of the libraries have coverage for each bin  

```{r}
sum_vec= apply(window_200_3lib[,4:6],1,function(x)sum(x>=1))
window_200_3lib= cbind(window_200_3lib, sum_vec)


```
Explore the results: 

```{r}
bin_0= sum(sum_vec==0)
bin_1= sum(sum_vec==1)
bin_2= sum(sum_vec==2)
bin_3= sum(sum_vec==3)

prop0=bin_0/x
prop1=bin_1/x
prop2=bin_2/x
prop3=bin_3/x

barplot_prop=(barplot(c(prop1, prop2, prop3),names = c("1 bin", "2 bins", "3 bins"), main="Proportion of bins with coverage in 3 libaries", ylab="proportion", xlab="library" ))

prop_vec=c(prop0,prop1, prop2, prop3)
names_vec= c("0 bins","1 bin", "2 bins", "3 bins")

prop_table=rbind(names_vec,prop_vec)
prop_table
```




### Perform on mayer data or multiple lanes  
```{bash, eval=FALSE}
#!/bin/bash

#SBATCH --job-name=window_200_cov_mayer
#SBATCH --time=8:00:00
#SBATCH --partition=broadwl
#SBATCH --mem=50G
#SBATCH --tasks-per-node=4
#SBATCH --mail-type=END

module load bedtools

bedtools coverage -counts -a /project2/gilad/briana/Net-seq/genome_bed/hg19_200bp_window.bed -b /project2/gilad/briana/mayer.data/mayer_hek/data/bed/mayer_hek-sort.chr.bed > /project2/gilad/briana/mayer.data/mayer_hek/data/window_200_cov_mayer_hek.txt
```


Not enough memory  

### Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
