---
title: "Verify bam"
author: "Briana Mittleman"
date: 2018-04-08
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->


I will verify the bam ids for the individuals in Net4.  

*add verify bam to conda env  
*create script to take any bam in the sort folder  
*run script with vcf in genome annotation directory  



```{bash, eval=FALSE}
# add to env. file
- verifybamid
#remove chr tag  
cat snps.hg19.exons.vcf  |sed 's/^chr//' > snps.hg19.exons.no_chr.vcf


```

Create the script to take in any bam files from net 4  
```{bash, eval=FALSE}
#!/bin/bash


#SBATCH --job-name=verify
#SBATCH --output=verify_sbatch.out
#SBATCH --error=verify_sbatch.err
#SBATCH --time=8:00:00
#SBATCH --partition=broadwl
#SBATCH --mem=36G
#SBATCH --mail-type=END

module load Anaconda3  

source activate net-seq 

sample=$1

describer=$(echo ${sample} | sed -e 's/.*\YG-SP-//' | sed -e "s/-sort.bam$//")


verifyBamID --vcf /project2/gilad/briana/genome_anotation_data/snps.hg19.exons.no_chr.vcf --bam $1 --best --ignoreRG --out /project2/gilad/briana/Net-seq-pilot/output/verifyBAM/${describer}.verify  


```

run on :   
*/project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-18497-2018-2-26_S3_L008_R1_001-sort.bam 

*/project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-18500-2018-2-26_S5_L008_R1_001-sort.bam  
*/project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-18853-2018-2-26_S8_L008_R1_001-sort.bam

*/project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-18870-2018-2-26_S6_L008_R1_001-sort.bam

*/project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-19209-2018-2-26_S4_L008_R1_001-sort.bam

*/project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-19223-2018-2-26_S2_L008_R1_001-sort.bam

*/project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-19225-2018-2-26_S7_L008_R1_001-sort.bam

*/project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-19238-2018-2-26_S1_L008_R1_001-sort.bam


  2 of the jobs timed out:  
  
  18853
  18870
  
  
mismatch: 19238 == 19226


Run this on lane 2 lines and see if I get the same results:  

* /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-18497-2018-2-26_S1_L008_R1_001_lane2-sort.bam  
* /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-18500-2018-2-26_S2_L008_R1_001_lane2-sort.bam  
* /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-18853-2018-2-26_S7_L008_R1_001_lane2-sort.bam  
* /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-18870-2018-2-26_S8_L008_R1_001_lane2-sort.bam  
* /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-19209-2018-2-26_S3_L008_R1_001_lane2-sort.bam  
* /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-19223-2018-2-26_S4_L008_R1_001_lane2-sort.bam  
* /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-19225-2018-2-26_S5_L008_R1_001_lane2-sort.bam  
* /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET4-19238-2018-2-26_S6_L008_R1_001_lane2-sort.bam  


More time out issues- Try subseting the bam file  


/project2/gilad/briana/Net-seq-pilot/data/sort/tenperc_YG-SP-NET4-18853-2018-2-26_S8_L008_R1_001-sort.bam

/project2/gilad/briana/Net-seq-pilot/data/sort/tenperc_YG-SP-NET4-18870-2018-2-26_S6_L008_R1_001-sort.bam

Try making the lane 2 files smaller to run them:

* /project2/gilad/briana/Net-seq-pilot/data/sort/tenperc_YG-SP-NET4-18853-2018-2-26_S7_L008_R1_001_lane2-sort.bam  

* /project2/gilad/briana/Net-seq-pilot/data/sort/tenperc_YG-SP-NET4-18870-2018-2-26_S8_L008_R1_001_lane2-sort.bam

* /project2/gilad/briana/Net-seq-pilot/data/sort/twentyperc_YG-SP-NET4-18497-2018-2-26_S1_L008_R1_001_lane2-sort.bam

* /project2/gilad/briana/Net-seq-pilot/data/sort/twentyperc_YG-SP-NET4-19209-2018-2-26_S3_L008_R1_001_lane2-sort.bam  

* /project2/gilad/briana/Net-seq-pilot/data/sort/twentyperc_YG-SP-NET4-19223-2018-2-26_S4_L008_R1_001_lane2-sort.bam

Conclusion: The lines are the expected individuals. The most likley explanation is a label swap on the liens in the fridge vs. the lines the core has.  


## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
