---
title: "Explore UMI Usage in Netseq1 libary"
author: "Briana Mittleman"
date: 2017-11-08
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

In this analysis I will explore the UMI usage in the Net-Seq1 library. Due to low read counts in the total sample, I will exclude this sample from the anaysis.  

This code is used to create a text file that I can explore in R. It has a list of all of the UMIs used for the sample sorted by usage with the number of times each is used. This is run before the duduplication step.   

```{bash, eval=FALSE}
samtools view {file} | tr "_" "\t" | cut -f 2 | sort | uniq -c > ../../output/UMI_{file}_stat.txt
```


All files have been create. Will import to R when I can mount midway on my computer.  
<!-- Insert the session information into the document -->
```{r session-info}
```
