---
title: "Explore UMI Usage in Netseq1 libary"
author: "Briana Mittleman"
date: 2017-11-08
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

In this analysis I will explore the UMI usage in the Net-Seq1 library. Due to low read counts in the total sample, I will exclude this sample from the analysis.  

This code is used to create a text file that I can explore in R. It has a list of all of the UMIs used for the sample sorted by usage with the number of times each is used. This is run before the duduplication step.   

```{bash, eval=FALSE}
samtools view {file} | tr "_" "\t" | cut -f 2 | sort | uniq -c > ../../output/UMI_{file}_stat.txt
```

###Packages  
```{r}
library("tidyr")
library("dplyr")
library("ggplot2")
library("seqLogo")
library("Biostrings")
require(Biostrings)
```




###Input data  

```{r}
#18486_dep
UMI_18486_dep = read.delim(file="../data/UMI_18486_dep_stat.txt", header=FALSE, stringsAsFactors = FALSE)
colnames(UMI_18486_dep) <- "UMI"
UMI_18486_dep= data.frame(sapply(UMI_18486_dep, trimws), stringsAsFactors = FALSE)
UMI_18486_dep= separate(data=UMI_18486_dep, col = UMI, into= c("number", "umi"), sep="\\s+")
UMI_18486_dep$number= as.numeric(UMI_18486_dep$number)
UMI_18486_dep= arrange(UMI_18486_dep, desc(number))


#18508 dep
UMI_18508_dep = read.delim(file="../data/UMI_18508_dep_stat.txt", header=FALSE, stringsAsFactors = FALSE)
colnames(UMI_18508_dep) <- "UMI"
UMI_18508_dep= data.frame(sapply(UMI_18508_dep, trimws), stringsAsFactors = FALSE)
UMI_18508_dep= separate(data=UMI_18508_dep, col = UMI, into= c("number", "umi"), sep="\\s+")
UMI_18508_dep$number= as.numeric(UMI_18508_dep$number)
UMI_18508_dep= arrange(UMI_18508_dep, desc(number))

#18508 nondep
UMI_18508_nondep = read.delim(file="../data/UMI_18508_nondep_stat.txt", header=FALSE, stringsAsFactors = FALSE)
colnames(UMI_18508_nondep) <- "UMI"
UMI_18508_nondep= data.frame(sapply(UMI_18508_nondep, trimws), stringsAsFactors = FALSE)
UMI_18508_nondep= separate(data=UMI_18508_nondep, col = UMI, into= c("number", "umi"), sep="\\s+")
UMI_18508_nondep$number= as.numeric(UMI_18508_nondep$number)
UMI_18508_nondep= arrange(UMI_18508_nondep, desc(number))


#19238
UMI_19238_dep = read.delim(file="../data/UMI_19238_dep_stat.txt", header=FALSE, stringsAsFactors = FALSE)
colnames(UMI_19238_dep) <- "UMI"
UMI_19238_dep= data.frame(sapply(UMI_19238_dep, trimws), stringsAsFactors = FALSE)
UMI_19238_dep= separate(data=UMI_19238_dep, col = UMI, into= c("number", "umi"), sep="\\s+")
UMI_19238_dep$number= as.numeric(UMI_19238_dep$number)
UMI_19238_dep= arrange(UMI_19238_dep, desc(number))


#Mayer
UMI_mayer = read.delim(file="../data/UMI_mayer_stat.txt", header=FALSE, stringsAsFactors = FALSE)
colnames(UMI_mayer) <- "UMI"
UMI_mayer= data.frame(sapply(UMI_mayer, trimws), stringsAsFactors = FALSE)
UMI_mayer= separate(data=UMI_mayer, col = UMI, into= c("number", "umi"), sep="\\s+")
UMI_mayer$number= as.numeric(UMI_mayer$number)
UMI_mayer= arrange(UMI_mayer, desc(number))
```


####Plot the umi distributions  
```{r}
par(mfrow = c(2,3))
plot(UMI_18486_dep$number, ylab="UMI count", xlab="UMI", main="18486-dep distribution")
plot(UMI_18508_dep$number, ylab="UMI count", xlab="UMI", main="18508-dep distribution")
plot(UMI_18508_nondep$number, ylab="UMI count", xlab="UMI", main="1508- nondep distribution")
plot(UMI_19238_dep$number, ylab="UMI count", xlab="UMI", main="19238-dep distribution")
plot(UMI_mayer$number, ylab="UMI count", xlab="UMI", main="Mayer distribution")
```
Look at the top used UMI for each data set.   
```{r}
UMI_18486_dep[1:3,]
UMI_18508_dep[1:3,]
UMI_18508_nondep[1:3, ]
UMI_19238_dep[1:3,]
UMI_mayer[1:3,]

```
The top used UMIs are similar accross samples. This preference could be due to annealing temperatures.(Conversation with Po) All data sets show an overrepresentation of a few UMIs, I will remove the top 5 to get a better look at the distribution.   

```{r plot}
par(mfrow = c(2,3))
plot(UMI_18486_dep[6:5388,]$number, ylab="UMI count", xlab="UMI", main="18486-dep distribution -5")

plot(UMI_18508_dep[6:5471,]$number, ylab="UMI count", xlab="UMI", main="18508-dep distribution -5")

plot(UMI_18508_nondep[6:5535,]$number, ylab="UMI count", xlab="UMI", main="18508-nondep distribution -5")

plot(UMI_19238_dep[6:5699,]$number, ylab="UMI count", xlab="UMI", main="19328-dep distribution -5")

plot(UMI_mayer[6:6101,]$number, ylab="UMI count", xlab="UMI", main="Mayer distribution -5")
```

####Seq Logo Plots 

Use Biostrings to get the PMW then create the logoplots with seqlogo.  

```{r}
#source("https://bioconductor.org/biocLite.R")
#biocLite("seqLogo")
#source("http://bioconductor.org/biocLite.R")
#biocLite("Biostrings")
#set= DNAStringSet(UMI_18486_dep$umi)
#length(set)
#set.freq=data.frame(alphabetFrequency(set, baseOnly=T, as.prob=T))
#set_noN=set[set.freq$other==0,]
#length(set_noN)
#width(set_noN)
#x=consensusMatrix(set_noN) #problem here, getting 1024 for all
#freq_18486= PWM(x[1:4,])

#sum(UMI_18486_dep$number==0) > 0 : shows no UMIs are never used 

#seqLogo(freq_18486, ic.scale = TRUE, xaxis = TRUE, yaxis = TRUE, xfontsize = 15, yfontsize =15)

  
  
```
Try with a different package:  

```{r}
#library("devtools")
#install_github("omarwagih/ggseqlogo")
require(ggseqlogo)

cs1 = make_col_scheme(chars=c('A', 'T', 'C', 'G', 'N'), groups=c('A', 'T', 'C', 'G', 'N'), cols=c('red', 'blue', 'green', 'yellow', 'pink'))


par(mfrow = c(2,3))
ggseqlogo(UMI_18486_dep$umi, col_scheme=cs1)
ggseqlogo(UMI_18508_dep$umi, col_scheme=cs1)
ggseqlogo(UMI_18508_nondep$umi, col_scheme=cs1)
ggseqlogo(UMI_19238_dep$umi, col_scheme=cs1)
ggseqlogo(UMI_mayer$umi, col_scheme=cs1)





```
Does not look like we get overrepresentation of one letter at any particular location in the UMI.  

```{r}
test.seqs= c("ATGC", "TAGC", "ATGC", "ATGC")
ggseqlogo(test.seqs, col_scheme=cs1)

```



<!-- Insert the session information into the document -->
```{r session-info}
```
