---
title: "Assign PAS to genes to call QTLs"
author: "Briana Mittleman"
date: 2018-02-13
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->
###Match each PAS to its gene


What gene go with each pas: 
Goal: matrix with pas/gene by individual with percent usage of that pas compared to others in the gene.  

```{r}
library("dplyr")
library("tidyr")
library("ggplot2")
library("cowplot")
library("IRanges")
library("biomaRt")
```

Import PAS file:  
```{r}
all_files_cov= read.table(file="../data/all_files.APA500.coverage.bed", stringsAsFactors = FALSE, header = FALSE)
names(all_files_cov)= c("chr", "start", "end", "meta", "score", "strand", "NA18486", 
"NA18488", "NA18489", "NA18498", "NA18499", "NA18502","NA18505","NA18508","NA18510","NA18511","NA18517","NA18519",'NA18520',"NA18858",'NA18861','NA18867','NA18868','NA18870','NA18873','NA18907','NA18909','NA18910','NA18912','NA18916','NA18917','NA18923','NA18933','NA18934','NA19092','NA19093','NA19095','NA19096','NA19098','NA19099','NA19102','NA19107','NA19108','NA19113','NA19114','NA19116','NA19117','NA19118','NA19119','NA19121','NA19129','NA19130','NA19131','NA19137','NA19138','NA19141','NA19143','NA19144','NA19146','NA19147','NA19149','NA19150','NA19152','NA19153','NA19159','NA19160','NA19171','NA19172','NA19175','NA19184','NA19185','NA19189','NA19190','NA19197','NA19198','NA19200','NA19201','NA19204','NA19206','NA19207',"NA19209","NA19210","NA19213","NA19214","NA19222","NA19223","NA19225","NA19236","NA19247","NA19248","NA19256","NA19257")
```
The meta info for each PAS includes the chr and chr location.  
```{r}
meta_info= separate(all_files_cov, meta, c("chr", "strand","pos", "type" ), ":")[,4:7]
```


```{r}
genes=read.table(file="../data/RefSeqGenes.bed", stringsAsFactors = FALSE, skip=1)
genes=genes[,1:6]
names(genes)=c("chr", "start", "end", "name", "score", "strand")
```

I need the gene line where gene-chr' and gene-strand are the same as the line in the meta info table and the meta_info pos is between gene-start and gene-end. I will make a function to do this then loop the function over all PAS.  

```{r}
gene_at_pos=function(row){
  #takes in the row from meta_info 
  #relies on genes dataframe in environment
  chrom=as.character(row[1])
  pos=as.integer(row[3])
  st=as.character(row[2])
  gene_line= which(genes$strand==st & genes$chr==chrom & genes$start < pos & genes$end > pos)
  #condition for no genes
  if (length(gene_line)==0){
    return("NA")
  }
  #condition for 1 or more genes 
  else{
  return(genes[gene_line,"name"])
  }
} 



```

This function will return NA if there is no gene, if there is one or more it will create a list of genes the pas is in.  Next step is to loop this function over my whole meta_info data frame.  


```{r}
#uncomment to rerun:
#gene_names=apply(meta_info,1,gene_at_pos)

```

If this doesnt work I will try this in python where it is better at loops.  
It worked but here is code. 

```{python, eval=FALSE}

#List = open("filename.txt").readlines()
import pandas as pd 


genes=pd.read_csv("genes.csv")
meta_info= pd.read_csv("meta_info.csv")

def gene_at_pos_py(row):
  """males a gene list for each row in the meta data, takes in a list of the row"""
  chrom=row[0]
  pos=row[1]
  strand=row[2]
  gene=genes[genes[["strand"]]==strand and genes[["chr"]]==chrom and genes[["strart"]] < pos and genes[["end"]] > pos, "name"]
  return(gene)
  
gene_list=[] 
for i, r in meta_info.iterrows():
  x= gene_at_pos_py(r)
  gene_list=[gene_list,x]

df_gene_list=pd.DataFrame(gene_list, columns=["gene"])

df_gene_list.to_csv("gene_list.csv")
  


```

This works but some of the PAS are in multiple genes. I downloaded the BED file(different poly(A)site annotation) file from  http://polyasite.unibas.ch/#5 . It is in /project2/gilad/briana/apa_sites/rnaseq_LCL/clusters_fullAnno.bed. 

I will use this to make a dictionary with the keys as genes and the values as the pas sites that are in that gene. The second to last column has the information I want. I will then use this to create a new bed file where the distances are either to the next pas in that gene or 500bp. This will give more precision for seeing choice rather than overlap as I saw before. 


ALso for future use: https://www.gencodegenes.org/releases/19.html This is the gene annotations I should use.  

Script from Yang: This is /project2/gilad/briana/apa_sites/rnaseq_LCL/parse_clusters.py  
```{python, eval=FALSE }

#!/usr/bin/env python

dic = {}
for ln in open("clusters_withTissueInfo.bed"):
    gene = ln.split()[-2]
    celltype = ln.split()[-1].split(";")
    
    # Change this depending on how conservative you want to be
    if "B_LCL_cells" not in celltype and "native_B_cells" not in celltype: continue

    if gene == ".": continue
    
    chrom, s, e, annot, support, strand = ln.split()[:6]
    if annot.split(":")[-1] in ["AI", "AE"]: continue
    if gene not in dic:
        dic[gene] = []
    dic[gene].append((int(s),int(e),strand, ln.split()[:4]))

cutoff = 500
for g in dic:
    pas = dic[g]
    if len(pas) <= 1: continue
    pas.sort()
    strand = pas[0][2]
    N = 1
    if strand == "+":
        print "%s.PAS%d"%(g,N), pas[0][1]-cutoff, pas[0][1], pas[0]
    else:
        pas.reverse()
        print "%s.PAS%d"%(g,N), pas[0][0], pas[0][0]+cutoff, pas[0]
    for i in range(len(pas)-1):
        N += 1
        if strand == "+":
            if (pas[i+1][0] - pas[i][1]) > cutoff:
                # the next one is further than the cutoff
                print "%s.PAS%d"%(g,N), chrom,  pas[i+1][1]-cutoff, pas[i+1][1], pas[i+1]
            else:
                print "%s.PAS%d"%(g,N), chrom, pas[i][1], pas[i+1][1], pas[i+1]
        else:
            if -(pas[i+1][0] - pas[i][0]) > cutoff:
                # the next one is further than the cutoff
                print "%s.PAS%d"%(g,N), chrom, pas[i+1][0], pas[i+1][0]+cutoff, pas[i+1]
            else:
                print "%s.PAS%d"%(g,N), chrom, pas[i+1][0], pas[i][0], pas[i+1]
```



to add to this script: 

wrtie out the dic to a dataframe. Also the print is going to standard out- would want to change that in future.  



## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
