---
title: "Initial Data Exploration Netseq1"
author: "Brina Mittleman"
date: 2017-11-06
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

I will use this analysis to look at inital data QC and points of interests.  

First I looked at the number of reads that mapp to the genome before and after deduplication UMI steps.  


Sorted Bam files:  
  388305 Undetermined_S0_R1_001-sort.bam  
   5111260 YG-SP-NET1-18486-dep-2017-10-13_S4_R1_001-sort.bam  
       688 YG-SP-NET1-18486-total-2017-10-13_S5_R1_001-sort.bam  
   7775502 YG-SP-NET1-18508-dep-2017-10-13_S2_R1_001-sort.bam  
   8408777 YG-SP-NET1-18508-nondep-2017-10-13_S3_R1_001-sort.bam  
  12164551 YG-SP-NET1-Unk1_S6_R1_001-sort.bam  

Deduplicated Bam files:  
    51460 Undetermined_S0_R1_001-sort.dedup.bam  
   211005 YG-SP-NET1-18486-dep-2017-10-13_S4_R1_001-sort.dedup.bam  
      205 YG-SP-NET1-18486-total-2017-10-13_S5_R1_001-sort.dedup.bam  
   252074 YG-SP-NET1-18508-dep-2017-10-13_S2_R1_001-sort.dedup.bam  
   275790 YG-SP-NET1-18508-nondep-2017-10-13_S3_R1_001-sort.dedup.bam  
   252305 YG-SP-NET1-Unk1_S6_R1_001-sort.dedup.bam  


```{r}
sort=c(388305,5111260,688, 7775502,8408777, 12164551)
dedup= c(51460, 211005, 205, 252074 ,275790,252305 )
diff= sort - dedup
# % change
perc_diff= (sort-dedup)/sort
UMI_diff= rbind(sort, dedup, diff, perc_diff)


```



## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
