---
title: "Work on extracting mapping info from bam files"
author: "Briana Mittleman"
date: 2017-11-16
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```


### Mapped stats  


Goal: Extract the number of bases that mapped and were soft clipped from bam files and make a histogram  

Look first at the original bam files from the snake mapping.  

To look at bam files in python, use pysam. I added this to my environment.  

Process: 

* Python Script: for simplicity at first, this file is called get_mapped.py and is in the /project2/gilad/briana/Net-seq/Net-seq1/data/sort/ directory. The bam file needs to have a bai file in teh same directory to work with the pysam program  

```{python, eval=FALSE}
#!/usr/bin/env python
import sys
import pysam
import re


mapped_num = open("mapped_18486_dep.txt", "w")
file_bam_open= open("/project2/gilad/briana/Net-seq/Net-seq1/data/sort/YG-SP-NET1-18486-dep-2017-10-13_S4_R1_001-sort.bam", "r")
file_bam= pysam.AlignmentFile(file_bam_open, "rb")
def get_mapped(file):
  mapped=[]
  for read in file.fetch():
      read= str(read)
      cigar= read.split()[5] #python starts at 0
      num= re.findall("\d+M", cigar) #this gives me each "##M" in the cigar
      for i in num:
        mapped.append(i[:-1])
  return(mapped)

a= get_mapped(file_bam)

mapped_num.write("\n".join(a))

mapped_num.close()

  
    
```


What I want: 

6th column (sep by tab) of the line. ex: 7S23M14S. I want the all the numbers before the M in this string.  


Pull the txt file with all the numbers into R and make a histogram.  
```{bash, eval=FALSE}
scp brimittleman@midway2.rcc.uchicago.edu:/project2/gilad/briana/Net-seq/Net-seq1/data/sort/mapped_18486_dep.txt .

```

```{r}
mapped=read.csv("../data/mapped_18486_dep.txt", header=FALSE)
map.vec= as.vector(mapped[,1])
hist(map.vec, xlab="Bases", main="Histogram of mapped reads from cigar string")
summary(map.vec)
```

Change the code so I only add the max mapped value from each read to the file.  get_mapped_max.py  

```{bash, eval= FALSE}
#!/usr/bin/env python
import sys
import pysam
import re 


mapped_num = open("mapped_18486_dep_max.txt", "w")

file_bam_open= open("/project2/gilad/briana/Net-seq/Net-seq1/data/sort/YG-SP-NET1-18486-dep-2017-10-13_S4_R1_001-sort.bam", "r")
file_bam= pysam.AlignmentFile(file_bam_open, "rb")

def get_mapped(file):
  mapped=[]
  for read in file.fetch():
      read=str(read)
      cigar= read.split()[5] #python starts at 0
      num= re.findall("\d+M", cigar) #this gives me each "##M" in the cigar
      m=[]      
      for i in num:
        m.append(i[:-1])
      mapped.append(max(m))
  return(mapped)


a=get_mapped(file_bam)
  
mapped_num.write("\n".join(a))  

mapped_num.close()
```

```{r}
mapped.max=read.csv("../data/mapped_18486_dep_max.txt", header=FALSE)
map.vec.max= as.vector(mapped.max[,1])
hist(map.vec.max, xlab="Bases", main="Histogram of max mapped reads from cigar string")
summary(map.vec.max)
```

###Soft Clip stats  

I will change the code so it looks for the digits before the S in the cigar string.  

```{python, eval=FALSE}
#!/usr/bin/env python
import sys
import pysam
import re


clip_num = open("clip_18486_dep.txt", "w")
file_bam_open= open("/project2/gilad/briana/Net-seq/Net-seq1/data/sort/YG-SP-NET1-18486-dep-2017-10-13_S4_R1_001-sort.bam", "r")
file_bam= pysam.AlignmentFile(file_bam_open, "rb")
def get_clip(file):
  clip=[]
  for read in file.fetch():
      read= str(read)
      cigar= read.split()[5] #python starts at 0
      num= re.findall("\d+S", cigar) #this gives me each "##S" in the cigar
      for i in num:
        clip.append(i[:-1])
  return(clip)

c= get_clip(file_bam)

clip_num.write("\n".join(c))

clip_num.close()

  
    
```


```{r}
clip=read.csv("../data/clip_18486_dep.txt", header=FALSE)
clip.vec= as.vector(clip[,1])
hist(clip.vec, xlab="Bases", main="Histogram of clipped reads from cigar string")
summary(clip.vec)
```



### Make this code general 

### Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
