---
title: "Initial Data exploration of Net-3"
author: "Briana Mittleman"
date: 2018-02-14
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

This analysis is to look at the quality of the library net-3. This has the first 8 libraries from the 16 pilot libraries. 

* 18505  

* 18508  

* 18486  

* 19239  

* 19141  

* 19193  

* 19257  

* 19128  

The first step is to run the raw reads through my snakefile. To do this I have to change the project directory in the /project2/gilad/briana/net_seq_pipeline/config.yaml to /project2/gilad/briana/Net-seq/Net-seq3/ .   

The reads will go in: /project2/gilad/briana/Net-seq/Net-seq3/data/fastq/  

I first use gunzip to unzip all of the fastq files then I submit the snakemake file from /project2/gilad/briana/net_seq_pipeline with nohup scripts/submit-snakemake.sh

Look at number of reads, mapped reads, deduplicated reads.  

'samtools view -c -F 4'

```{r}
libraries=c("18486", "18505", "18508", "19128", "19141", "19193", "19239", '19257')
fastq=c( 34342214,42959246,205654644, 51413661,211367408,52841852,54253650,45506210)
mapped=c(14018943,23607050,26532568,38084941,28165596,37084191,37095436,26636660)
dedup= c(1446379, 1032174,1642314,2469438,1926300,2717515, 2361238, 1377712 )

read_count=rbind(fastq,mapped,dedup)
colnames(read_count)=libraries 


```

```{r}
total_reads= sum(fastq)
total_reads
total_map= sum(mapped)
total_map
total_dedup= sum(dedup)
total_dedup

total_map/total_reads
total_dedup/total_map

```

Make a plot to look at this by line:  

```{r}
count_plot=barplot(as.matrix(read_count), main="Counts for coverage and complexity",
  xlab="Library", col=c("lightskyblue2","dodgerblue1","navy"),
    ylab="Read counts")
legend("topright", legend = c("total", "mapped", "UMI"), col=c("lightskyblue2","dodgerblue1","navy"), pch=20, cex = .75)
```


Look at this by proportions:  

```{r}
percent_mapped= mapped/fastq
percent_UMI= dedup/fastq
percent_mapped= percent_mapped - percent_UMI
percent_not_mapped= 1- percent_mapped - percent_UMI


prop=rbind(percent_not_mapped, percent_mapped, percent_UMI)
colnames(prop)= libraries

prop_plot=barplot(as.matrix(prop), main="Proportions for coverage and complexity",
  xlab="Library", col=c("lightskyblue2","dodgerblue1","navy"),
    ylab="Proportion of sequenced reads")
legend("bottomright", legend = c("un-mapped", "mapped", "UMI"), col=c("lightskyblue2","dodgerblue1","navy"), pch=20, cex = 0.75)


```


```{r}
summary(mapped)
summary(percent_mapped)
summary(percent_not_mapped)
```

I will now use the get_mapped.py script from the previous analysis to see how long the mapped reads are. I copied it to /project2/gilad/briana/Net-seq/Net-seq3/code. The code takes in sorted bam file and an output text file. I will create a sbatch script to run this on all 8 files. This file is called wrap_get_mapped.sh and is in the same code directory.  


```{bash, eval=FALSE}
#!/bin/bash


#SBATCH --job-name=wrap_get_map
#SBATCH --time=8:00:00
#SBATCH --partition=gilad
#SBATCH --mem=16G
#SBATCH --mail-type=END

module load Anaconda3

source activate net-seq  

python /project2/gilad/briana/Net-seq/Net-seq3/code/get_mapped.py /project2/gilad/briana/Net-seq/Net-seq3/data/sort/YG-SP-NET3-18486-2018-1-8_S3_L008_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq3/output/mapped_stats_18486.txt

python /project2/gilad/briana/Net-seq/Net-seq3/code/get_mapped.py /project2/gilad/briana/Net-seq/Net-seq3/data/sort/YG-SP-NET3-18505-2018-1-8_S1_L008_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq3/output/mapped_stats_18505.txt

python /project2/gilad/briana/Net-seq/Net-seq3/code/get_mapped.py /project2/gilad/briana/Net-seq/Net-seq3/data/sort/YG-SP-NET3-18508-2018-1-8_S2_L008_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq3/output/mapped_stats_18508.txt

python /project2/gilad/briana/Net-seq/Net-seq3/code/get_mapped.py /project2/gilad/briana/Net-seq/Net-seq3/data/sort/YG-SP-NET3-19128-2018-1-8_S8_L008_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq3/output/mapped_stats_19128.txt  


python /project2/gilad/briana/Net-seq/Net-seq3/code/get_mapped.py /project2/gilad/briana/Net-seq/Net-seq3/data/sort/YG-SP-NET3-19141-2018-1-8_S5_L008_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq3/output/mapped_stats_19141.txt 

python /project2/gilad/briana/Net-seq/Net-seq3/code/get_mapped.py /project2/gilad/briana/Net-seq/Net-seq3/data/sort/YG-SP-NET3-19193-2018-1-8_S6_L008_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq3/output/mapped_stats_19193.txt 

python /project2/gilad/briana/Net-seq/Net-seq3/code/get_mapped.py /project2/gilad/briana/Net-seq/Net-seq3/data/sort/YG-SP-NET3-19239-2018-1-8_S4_L008_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq3/output/mapped_stats_19239.txt 

python /project2/gilad/briana/Net-seq/Net-seq3/code/get_mapped.py /project2/gilad/briana/Net-seq/Net-seq3/data/sort/YG-SP-NET3-19257-2018-1-8_S7_L008_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq3/output/mapped_stats_19257.txt 



```

I will now make histograms showing the number of reads that map from the cigar strings.  

```{r}
#pull in data:  

map.vec.18486=read.csv("../data/net-3-readmap/mapped_stats_18486.txt", header=FALSE)
map.vec.18505=read.csv("../data/net-3-readmap/mapped_stats_18505.txt", header=FALSE)
map.vec.18508=read.csv("../data/net-3-readmap/mapped_stats_18508.txt", header=FALSE)
map.vec.19128=read.csv("../data/net-3-readmap/mapped_stats_19128.txt", header=FALSE)
map.vec.19141=read.csv("../data/net-3-readmap/mapped_stats_19141.txt", header=FALSE)
map.vec.19193=read.csv("../data/net-3-readmap/mapped_stats_19193.txt", header=FALSE)
map.vec.19239=read.csv("../data/net-3-readmap/mapped_stats_19239.txt", header=FALSE)
map.vec.19257=read.csv("../data/net-3-readmap/mapped_stats_19257.txt", header=FALSE)
#pull in mayer as well

map.vec.mayer=read.csv("../data/mapped_mayer.txt", header=FALSE)
```

```{r}
#make histograms

par(mfrow=c(3,3))
hist((as.numeric(map.vec.18486$V1)), xlab="Bases", main="Histogram of 18486 mapped reads")
 hist((as.numeric(map.vec.18505$V1)), xlab="Bases", main="Histogram of 18505 mapped reads")
hist((as.numeric(map.vec.18508$V1)), xlab="Bases", main="Histogram of 18508 mapped reads")
hist((as.numeric(map.vec.19128$V1)), xlab="Bases", main="Histogram of 19128 mapped reads")
hist((as.numeric(map.vec.19141$V1)), xlab="Bases", main="Histogram of 19141 mapped reads")
hist((as.numeric(map.vec.19193$V1)), xlab="Bases", main="Histogram of 19193 mapped reads")
hist((as.numeric(map.vec.19239$V1)), xlab="Bases", main="Histogram of 19239 mapped reads")
hist((as.numeric(map.vec.19257$V1)), xlab="Bases", main="Histogram of 19257 mapped reads")
hist((as.numeric(map.vec.mayer$V1)), xlab="Bases", main="Histogram of Mayer mapped reads")
```

###Deep tools analysis:  

First I downloaded the gencode.hg19 gene gtf file. I will use bedops convert2bed. 
```{bash, eval=FALSE}
awk '{ if ($0 ~ "transcript_id") print $0; else print $0" transcript_id \"\";"; }' gencode.v19.annotation.gtf | gtf2bed - > gencode.v19.annotation.bed 

```

Deep tools code:  

```{bash, eval=FALSE}
#!/bin/bash


#SBATCH --job-name=deeptools_netseq
#SBATCH --time=8:00:00
#SBATCH --partition=gilad
#SBATCH --mem=16G
#SBATCH --mail-type=END
#SBATCH --output=deeptool_sbatch.out
#SBATCH --error=deeptools_sbatch.err

module load Anaconda3

source activate net-seq

bamCoverage -b /project2/gilad/briana/Net-seq/Net-seq3/data/sort/YG-SP-NET3-18486-2018-1-8_S3_L008_R1_001-sort.bam -o /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-18486.bw

computeMatrix reference-point -S /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-18486.bw -R /project2/gilad/briana/Net-seq/Net-seq3/gencode.v19.annotation.bed --referencePoint TSS -b 100 -a 100 -out /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-18486.gz

plotHeatmap --sortRegions descend --refPointLabel "TSS" -m /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-18486.gz  -out /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-18486.png
```

To look at TES I will change the reference point to TES. This script is also in the code file as deep_tools_TES_net18486.sh.  


```{bash, eval=FALSE}
#!/bin/bash


#SBATCH --job-name=deeptools_TES_netseq
#SBATCH --time=8:00:00
#SBATCH --partition=gilad
#SBATCH --mem=16G
#SBATCH --mail-type=END
#SBATCH --output=deeptool_TES_sbatch.out
#SBATCH --error=deeptools_TES_sbatch.err

module load Anaconda3

source activate net-seq

#the bw file has already been created

computeMatrix reference-point -S /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-18486.bw -R /project2/gilad/briana/Net-seq/Net-seq3/gencode.v19.annotation.bed --referencePoint TES -b 100o -a 1000 -out /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-TES-18486.gz

plotHeatmap --sortRegions descend --refPointLabel "TSS"  -m /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-TES-18486.gz  -out /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-TES-18486.png
```

Do this for DNA hypersensitivity clusters as well.  This script is in the code file as deep_tools_DHS_net18486.sh. 

```{bash, eval=FALSE}
#!/bin/bash


#SBATCH --job-name=deeptools_DHS_netseq
#SBATCH --time=8:00:00
#SBATCH --partition=gilad
#SBATCH --mem=16G
#SBATCH --mail-type=END
#SBATCH --output=deeptool_DHS_sbatch.out
#SBATCH --error=deeptools_DHS_sbatch.err

module load Anaconda3

source activate net-seq

#the bw file has already been created

computeMatrix reference-point -S /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-18486.bw -R /project2/gilad/briana/Net-seq/Net-seq3/wgEncodeRegDnaseClusteredV3.bed -b 1000 -a 1000 -out /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-dhs-18486.gz

plotHeatmap --sortRegions descend --refPointLabel "DHS" -m /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-dhs-18486.gz  -out /project2/gilad/briana/Net-seq/Net-seq3/output/deeptools/net-seq-dhs-18486.png

```

I am running these and 1 more looking at the TSS but at 1000 base pairs on each side.  

## Session information
 


<!-- Insert the session information into the document -->
```{r session-info}
```
