---
title: "Coverage in gene regions"
author: "Briana Mittleman"
date: 2017-11-20
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

The goal of this analysis is too look at read coverage in genes/exons/and in genes + promoter regions for my Net-seq data and the Mayer data. This will help me understand if the problem with this data is coverage. 

I have downloaded 3 bed files from the UCSC table browser:  

* Ref seq genes  

* Ref seq genes + 250 upstream  

* Ref seq exons  


I will use the bedtools coverage function. Documentation is below:  

http://bedtools.readthedocs.io/en/latest/content/tools/coverage.html  

* a bed file for the genes/exons  
* bam files for my data and the mayer data  

```{bash, eval=FALSE}

bedtools coverage -a <FILE> \
                             -b <FILE1, FILE2, ..., FILEN>
```


Write a bash script for genes overlap:  genome_overlap.sh
```{bash, eval=FALSE}
#!/bin/bash

#SBATCH --job-name=bedtools_coverage
#SBATCH --time=8:00:00
#SBATCH --partition=broadwl
#SBATCH --mem=8G
#SBATCH --tasks-per-node=4 

#$1 reference to use 


bedtools coverage -a $1 -b /project2/gilad/briana/Net-seq/Net-seq1/data/sort/YG-SP-NET1-18486-dep-2017-10-13_S4_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq1/data/sort/YG-SP-NET1-18508-dep-2017-10-13_S2_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq1/data/sort/YG-SP-NET1-18508-nondep-2017-10-13_S3_R1_001-sort.bam /project2/gilad/briana/Net-seq/Net-seq1/data/sort/YG-SP-NET1-Unk1_S6_R1_001-sort.bam /project2/gilad/briana/Net-seq/data/sort/SRR1575922-sort.bam 

#> to a txt file  


bedtools coverage -a ref_seq_gene_hg19 -b /project2/gilad/briana/Net-seq/Net-seq1/data/net1_18486_dep_dedup_chr.bed -hist  > gene_coverage_18486_dedup_hist.txt

```


Try with only 1 file first.  


```{bash, eval=FALSE}
 #sort -k1,1 -k2,2n ref_seq_gene_hg19 > ref_seq_gene_hg19_sorted.bed

```


Try with /project2/gilad/briana/Net-seq/Net-seq1/data/net1_18486_dep_dedup_chr.bed  

This works but it is for the deduplicated file. I am going to do the sorted files first. I need to convert the sorted bam files to bed files. All of the sorted bed files with the chr label are in data/bed  

```{bash, eval=FALSE}
bedtools bamtobed [OPTIONS] -i <BAM>
awk '$0="chr"$0' file > new_file 
```


Not sure what column is which.... need to look into the output more  

```{r}
gene_coverage_18486_dedup= read.csv("../data/gene_coverage_18486_dedup_hist.txt", header=FALSE, sep="\t")
```






## Session information

<!-- Insert the session information into the document -->
```{r session-info}

```
