---
title: "Recreate Figures with my data"
author: "Briana Mittleman"
date: 2018-03-13
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

This analysis is to recreate some of the figures from the Mayer paper using my data. 

```{r}
library(dplyr)
library(ggplot2)
library(workflowr)
library(gplots)
library(RColorBrewer)
library(scales)
library(reshape2)
```



###Fig1D

Correlation between 2 biological replicates for netseq gene counts. 'The data set with higher coverage was randomly downsampled to match
the total number of reads of the other data set.' 


First I will do this pre-filtering.  
```{r}
gene_cov_18486= read.table("../data/NET3-18486.gene.coverage.bed")
colnames(gene_cov_18486)= c("chr", "start", "end", "gene", "score", "strand", "count")
gene_cov_18505= read.table("../data/NET3-18505.gene.coverage.bed")
colnames(gene_cov_18505)= c("chr", "start", "end", "gene", "score", "strand", "count")
```

Sum for each of the counts:

```{r}
sum(gene_cov_18486$count)
sum(gene_cov_18505$count)
```

```{r}

plot(gene_cov_18486$count~gene_cov_18505$count, ylim=c(0,50000), xlim=c(0,50000))
```


Change to RPKM: 
divide by million of reads in the library and length :  

18486: mapped reads:  65189389
18505: mapped reads: 52507749

```{r}

mapped_18486_mil= 65189389 / 10^6
mapped_18505_mil= 52507749 / 10^6


gene_cov_18486 =gene_cov_18486 %>% mutate(K_length= (end - start)/100) %>% mutate(rpkm=.25 + count/(K_length * mapped_18486_mil)) 



gene_cov_18505 =gene_cov_18505 %>% mutate(K_length= (end - start)/100) %>% mutate(rpkm= .25 +count/(K_length * mapped_18505_mil))
```

Plot again:  


```{r}
plot(log10(gene_cov_18486$rpkm) ~log10(gene_cov_18505$rpkm), ylab="log10 RPKM reads 18486", xlab="log10 RPKM reads 18505", main="Fig 1D recreation")
abline(lm(log10(gene_cov_18486$rpkm) ~ log10(gene_cov_18505$rpkm)), col="blue")
```


correlation:  

```{r}
cor(log10(gene_cov_18486$rpkm),log10(gene_cov_18505$rpkm))
```




###Fig7b  

####Find top exons  

Create the exon file from gencode.v19.annotation.bed. Filter the exons.    

```{bash, eval=FALSE}
awk '/exon/' gencode.v19.annotation.gtf > gencode.v19.exon.annotation.gtf
```
Use featureCounts to quantify counts in these exons for 18486.  


```{bash,eval=FALSE}
#!/bin/bash

#SBATCH --job-name=exon_cov
#SBATCH --time=8:00:00
#SBATCH --output=exon_cov.out
#SBATCH --error=exon_cov.err
#SBATCH --partition=broadwl
#SBATCH --mem=20G
#SBATCH --mail-type=END

module load Anaconda3  

source activate net-seq 

#input is a bed file 
sample=$1


describer=$(echo ${sample} | sed -e 's/.*\YG-SP-//' | sed -e "s/_combined_Netpilot-sort.bam$//")


featureCounts -T 5 -a /project2/gilad/briana/genome_anotation_data/gencode.v19.exon.annotation.gtf -t exon -g exon_id -o /project2/gilad/briana/Net-seq-pilot/data/exon_cov/${describer}_combined_Netpilot-sort.exon.cov.txt $1


```

Run on  /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET3-18486_combined_Netpilot-sort.bam

Filter the exons I want to use for the analsis: 

* convert to RPKM (divide by length of the exon and by library read)


```{r}
exon_cov_18486= read.table("../data/NET3-18486_combined_Netpilot-sort.exon.cov.txt", header=TRUE)
colnames(exon_cov_18486)= c("ExonID", "Chr", "Start", "End", "Strand", "Length","Count" )
```

Convert to RPKM  

* mapped reads from the summary 

```{r}
mapped_reads= 40670322 + 9798066 + 14721001
exon_cov_18486= exon_cov_18486 %>% mutate(RPKM=(Count/(Length/1000))/(mapped_reads/10^6))

exon_cov_18486_no0= exon_cov_18486 %>% filter(RPKM!=0)
```


Plot the exon counts in log10(RPKM):  
```{r}
plot(log10(sort(exon_cov_18486_no0$RPKM, decreasing = TRUE)), col=ifelse(log10(sort(exon_cov_18486_no0$RPKM, decreasing = TRUE))>.28, "red", "black"), ylab = "log10 RPKM", xlab="Exon", main= "RPKM expression of exons 18486")



log10(sort(exon_cov_18486_no0$RPKM, decreasing = TRUE))[1990]
  
#39803*.05

```


Use top 5% - the top 10.  



```{r}
exon_cov_18486_no0_sort= exon_cov_18486_no0[order(exon_cov_18486_no0$RPKM, decreasing = TRUE),]
exon_cov_18486_no0_sort = exon_cov_18486_no0_sort %>% filter(log10(RPKM) > .28)

exon_list_table= exon_cov_18486_no0_sort[6:1911,1:6 ]


#write.table(exon_list_table,"../data/top5_exonlist.txt", col.names = TRUE, row.names = FALSE, quote = FALSE, sep="\t" )
```
File is: 
/project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486.bed

####Extract covereage at these exon junctions  

I want to make two seperate files, one for the 3' SS and one for the 5' splice site. 

```{bash, eval=FALSE}
less top5_exonlist2_18486.txt | awk ' {if($5 == "+") print($1 "\t" $2 "\t" $3 -40  "\t" $3 +40 "\t" $5 ); else print($1 "\t" $2 "\t"  $4 - 40 "\t" $4 +40  "\t" $5)}' > top5_exonlist_18486_fiveprime.txt 


less top5_exonlist2_18486.txt | awk ' {if($5 == "+") print($1 "\t" $2 "\t" $4 -40  "\t" $4 +40 "\t" $5 ); else print($1 "\t" $2 "\t"  $3 - 40 "\t" $3 + 40  "\t" $5)}' > top5_exonlist_18486_threeprime.txt 

```




**Problem: exon list has some exons twice in the same line**
```{bash,eval=FALSE}
cp top5_exonlist_18486.txt test.txt
awk '{print($2)}' test.txt| cut -d ";" -f1 > test.col2.txt 
awk '{print($3)}' test.txt| cut -d ";" -f1 > test.col3.txt 
awk '{print($4)}' test.txt| cut -d ";" -f1 > test.col4.txt
awk '{print($5)}' test.txt| cut -d ";" -f1 > test.col5.txt
awk '{print($1)}' test.txt  > test.col1.txt
awk '{print($6)}' test.txt  > test.col6.txt


paste -d "\t"  test.col1.txt test.col2.txt  test.col3.txt test.col4.txt test.col5.txt test.col6.txt > top5_exonlist2_18486.txt
```


Rerun aboove to seperate the 3' and 5'  


Remove the chr so I can match it to the genome coverage file:  

```{bash, eval=FALSE}
cat top5_exonlist_18486_fiveprime.txt | sed 's/chr//' > top5_exonlist_18486_fiveprime_noCHR.txt
 
cat top5_exonlist_18486_threeprime.txt | sed 's/chr//' > top5_exonlist_18486_threeprime_noCHR.txt
```


Make a bed file with just the first base of each of my reads from /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-sort.bed . For positive reads I use the start and the start +1 and for negative reads I use the end -1 and the end. I then will use bedtools coverage -d -s (force strandedness).     

* make top5_exonlist_18486_threeprime_noCHR.txt and top5_exonlist_18486_fiveprime_noCHR.txt bed format  
```{bash, eval=FALSE}
awk '{print ($2 "\t" $3 "\t" $4 "\t" $1 "\t.\t" $5)}' top5_exonlist_18486_threeprime_noCHR.txt| sort -k1,1 -k2,2n > top5_exonlist_18486_threeprime_noCHR.bed


awk '{print ($2 "\t" $3 "\t" $4 "\t" $1 "\t.\t" $5)}' top5_exonlist_18486_fiveprime_noCHR.txt| sort -k1,1 -k2,2n > top5_exonlist_18486_fiveprime_noCHR.bed


```

sort YG-SP-NET3-18486_combined_Netpilot-sort.bed the same way to make this easier.  

```{bash, eval=FALSE}
sort -k1,1 -k2,2n YG-SP-NET3-18486_combined_Netpilot-sort.bed > YG-SP-NET3-18486_combined_Netpilot-sort2.bed
```

* make the YG-SP-NET3-18486_combined_Netpilot-sort2.bed 1 bp resoluton with awk 
```{bash, eval=FALSE}
awk '{if($6 == "+") print($1 "\t" $2 "\t" $2 + 1  "\t" $4 "\t" $5 "\t" $6 ); else print($1 "\t" $3 -1 "\t" $3 "\t" $4 "\t" $5 "\t" $6 )}' YG-SP-NET3-18486_combined_Netpilot-sort2.bed > YG-SP-NET3-18486_combined_Netpilot-sort2-bp.bed
```

* bedtools script:  

```{bash, eval=FALSE}
#!/bin/bash

#SBATCH --job-name=ss_cov
#SBATCH --time=8:00:00
#SBATCH --output=ss_cov.out
#SBATCH --error=ss_cov.err
#SBATCH --partition=broadwl
#SBATCH --mem=40G
#SBATCH --mail-type=END

module load Anaconda3  

source activate net-seq 


bedtools coverage -d -s  -a /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_threeprime_noCHR.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-sort2-bp2.bed > /project2/gilad/briana/Net-seq-pilot/data/ss_cov/top5_exonlist_18486_threeprime_cov.txt 


bedtools coverage -d -s  -a /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_fiveprime_noCHR.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-sort2-bp2.bed > /project2/gilad/briana/Net-seq-pilot/data/ss_cov/top5_exonlist_18486_fiveprime_cov.txt 
```


####Import and group by exon  

```{r}
five_prime_cov=read.table("../data/top5_exonlist_18486_fiveprime_cov.txt")
colnames(five_prime_cov)= c("chr", "start", "end", "exon", "score","strand", "pos", "count")
three_prime_cov=read.table("../data/top5_exonlist_18486_threeprime_cov.txt")
colnames(three_prime_cov)= c("chr", "start", "end", "exon","score","strand", "pos", "count")
```

summarize on window position to make top plot  
```{r}
cov_bypos_pos= five_prime_cov %>% filter(strand=="+") %>% group_by(pos) %>% summarise(sum_pos=sum(count)) 
cov_bypos_neg= five_prime_cov %>% filter(strand=="-") %>% group_by(pos) %>% summarise(sum_pos=sum(count))
cov_bypos_neg_vec= rev(as.numeric(unlist(cov_bypos_neg[,2])))

cov_bypos=cbind(cov_bypos_pos, cov_bypos_neg_vec)

cov_bypos_all= cov_bypos %>% mutate(sum_by_pos=sum_pos + cov_bypos_neg_vec )
cov_bypos_all= cov_bypos_all %>% select(pos, sum_by_pos)

```
Plot it:  

```{r}
cov_bypos_all_long=melt(cov_bypos_all, id.vars = 'pos', value.name ='count' ) %>% filter(pos > 30 & pos< 50)

ggplot(cov_bypos_all_long,aes(pos,count)) + geom_line() + ggtitle("5' splice site")

```

3 prime end:  

```{r}
cov_bypos_pos_3= three_prime_cov %>% filter(strand=="+") %>% group_by(pos) %>% summarise(sum_pos=sum(count)) 
cov_bypos_neg_3= three_prime_cov %>% filter(strand=="-") %>% group_by(pos) %>% summarise(sum_pos=sum(count))
cov_bypos_neg_vec_3= rev(as.numeric(unlist(cov_bypos_neg_3[,2])))

cov_bypos_3=cbind(cov_bypos_pos_3, cov_bypos_neg_vec_3)

cov_bypos_all_3= cov_bypos_3 %>% mutate(sum_by_pos=sum_pos + cov_bypos_neg_vec_3 )
cov_bypos_all_3= cov_bypos_all_3 %>% select(pos, sum_by_pos)
```

```{r}
cov_bypos_all_long_3=melt(cov_bypos_all_3, id.vars = 'pos', value.name ='count' ) %>% filter(pos > 20 & pos< 60)

ggplot(cov_bypos_all_long_3,aes(pos,count)) + geom_line() + ggtitle("3' splice site") 

```




####Try without strand specificity  

-get rid of the highly expressed bins if one of these exons is in it.  

The script splicesite_cov2.sh is not strand specific on mapping coverage.  
```{bash, eval=FALSE}
#!/bin/bash

#SBATCH --job-name=ss_cov2
#SBATCH --time=8:00:00
#SBATCH --output=ss_cov2.out
#SBATCH --error=ss_cov2.err
#SBATCH --partition=broadwl
#SBATCH --mem=40G
#SBATCH --mail-type=END

module load Anaconda3  

source activate net-seq 


bedtools coverage -d  -a /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_threeprime_noCHR.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-sort2-bp2.bed > /project2/gilad/briana/Net-seq-pilot/data/ss_cov/top5_exonlist_18486_threeprime_cov2.txt 


bedtools coverage -d   -a /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_fiveprime_noCHR.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-sort2-bp2.bed > /project2/gilad/briana/Net-seq-pilot/data/ss_cov/top5_exonlist_18486_fiveprime_cov2.txt 
```


```{r}
five_prime_cov2=read.table("../data/top5_exonlist_18486_fiveprime_cov2.txt", stringsAsFactors = FALSE)
colnames(five_prime_cov2)= c("chr", "start", "end", "exon", "score","strand", "pos", "count")
three_prime_cov2=read.table("../data/top5_exonlist_18486_threeprime_cov2.txt")
colnames(three_prime_cov2)= c("chr", "start", "end", "exon","score","strand", "pos", "count")
```

```{r}
cov_bypos_pos2= five_prime_cov2 %>% filter(strand=="+") %>% group_by(pos) %>% summarise(sum_pos=sum(count)) 
cov_bypos_neg2= five_prime_cov2 %>% filter(strand=="-") %>% group_by(pos) %>% summarise(sum_pos=sum(count))
cov_bypos_neg_vec2= rev(as.numeric(unlist(cov_bypos_neg2[,2])))

cov_bypos2=cbind(cov_bypos_pos2, cov_bypos_neg_vec2)

cov_bypos_all2= cov_bypos2 %>% mutate(sum_by_pos=sum_pos + cov_bypos_neg_vec )
cov_bypos_all2= cov_bypos_all2 %>% select(pos, sum_by_pos)

```

Plot it:  

```{r}
cov_bypos_all_long2=melt(cov_bypos_all2, id.vars = 'pos', value.name ='count' )

ggplot(cov_bypos_all_long2,aes(pos,count)) + geom_line() + ggtitle("5' splice site, not SS")

```


3 prime end:  

```{r}
cov_bypos_pos2_3= three_prime_cov2 %>% filter(strand=="+") %>% group_by(pos) %>% summarise(sum_pos=sum(count)) 
cov_bypos_neg2_3= three_prime_cov2 %>% filter(strand=="-") %>% group_by(pos) %>% summarise(sum_pos=sum(count))
cov_bypos_neg_vec2_3= rev(as.numeric(unlist(cov_bypos_neg2_3[,2])))

cov_bypos2_3=cbind(cov_bypos_pos2_3, cov_bypos_neg_vec2_3)

cov_bypos_all2_3= cov_bypos2_3 %>% mutate(sum_by_pos=sum_pos + cov_bypos_neg_vec2_3 )
cov_bypos_all2_3= cov_bypos_all2_3 %>% select(pos, sum_by_pos)
```

```{r}
cov_bypos_all_long2_3=melt(cov_bypos_all2_3, id.vars = 'pos', value.name ='count' ) %>% filter(pos > 20 & pos< 60)

ggplot(cov_bypos_all_long2_3,aes(pos,count)) + geom_line() + ggtitle("3' splice site, not SS") 

```


####Filter out the locations in bins and small RNAs  
I will use the files I created in the create_blacklist analysis to filter the exon regions that fall in those locations. Use bedtools intersect:  

* /project2/gilad/briana/genome_anotation_data/top5_gen_wind200.tab.nochr.sort.bed   

* project2/gilad/briana/genome_anotation_data/snRNA.gencode.v19.nochr.bed  

* /project2/gilad/briana/genome_anotation_data/snoRNA.gencode.v19.nochr.bed  

* /project2/gilad/briana/genome_anotation_data/rRNA.gencode.v19.nochr.bed  


splicesite_cov2_filter.sh   
```{bash, eval=FALSE}
#!/bin/bash

#SBATCH --job-name=filt_exoncov
#SBATCH --time=8:00:00
#SBATCH --output=filt_exoncov_sbatch.out
#SBATCH --error=filt_exoncov_sbatch.err
#SBATCH --partition=broadwl
#SBATCH --mem=40G
#SBATCH --mail-type=END


module load Anaconda3  

source activate net-seq 

bedtools intersect -v -wa -a /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_fiveprime_noCHR.bed -b /project2/gilad/briana/genome_anotation_data/top5_gen_wind200.tab.nochr.sort.bed /project2/gilad/briana/genome_anotation_data/snRNA.gencode.v19.nochr.bed /project2/gilad/briana/genome_anotation_data/snoRNA.gencode.v19.nochr.bed /project2/gilad/briana/genome_anotation_data/rRNA.gencode.v19.nochr.bed > /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_fiveprime_noCHR_filter.bed

bedtools coverage -d  -a /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_fiveprime_noCHR_filter.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-sort2-bp2.bed > /project2/gilad/briana/Net-seq-pilot/data/ss_cov/top5_exonlist_18486_fiveprime_cov2_filter.txt 

bedtools intersect -v -wa -a /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_threeprime_noCHR.bed -b /project2/gilad/briana/genome_anotation_data/top5_gen_wind200.tab.nochr.sort.bed /project2/gilad/briana/genome_anotation_data/snRNA.gencode.v19.nochr.bed /project2/gilad/briana/genome_anotation_data/snoRNA.gencode.v19.nochr.bed /project2/gilad/briana/genome_anotation_data/rRNA.gencode.v19.nochr.bed > /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_threeprime_noCHR_filter.bed

bedtools coverage -d  -a /project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_threeprime_noCHR_filter.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-sort2-bp2.bed > /project2/gilad/briana/Net-seq-pilot/data/ss_cov/top5_exonlist_18486_threeprime_cov2_filter.txt 


```
This results in 464 3-prime and 445 5-prime exons. 


```{r}
five_prime_cov_F=read.table("../data/top5_exonlist_18486_fiveprime_cov2_filter.txt")
colnames(five_prime_cov_F)= c("chr", "start", "end", "exon", "score","strand", "pos", "count")
three_prime_cov_F=read.table("../data/top5_exonlist_18486_threeprime_cov2_filter.txt")
colnames(three_prime_cov_F)= c("chr", "start", "end", "exon","score","strand", "pos", "count")
```



```{r}
cov_bypos_pos_F= five_prime_cov_F %>% filter(strand=="+") %>% group_by(pos) %>% summarise(sum_pos=sum(count)) 
cov_bypos_neg2_F= five_prime_cov_F %>% filter(strand=="-") %>% group_by(pos) %>% summarise(sum_pos=sum(count))
cov_bypos_neg_vec_F= rev(as.numeric(unlist(cov_bypos_neg2_F[,2])))

cov_bypos_F=cbind(cov_bypos_pos_F, cov_bypos_neg_vec_F)

cov_bypos_all_F= cov_bypos_F %>% mutate(sum_by_pos=sum_pos + cov_bypos_neg_vec )
cov_bypos_all_F= cov_bypos_all_F %>% select(pos, sum_by_pos)

```

Plot it:  

```{r}
cov_bypos_all_long_F=melt(cov_bypos_all_F, id.vars = 'pos', value.name ='count' )

ggplot(cov_bypos_all_long_F,aes(pos,count)) + geom_line() + ggtitle("5' splice site filtered exons")

```


3 prime end:  

```{r}
cov_bypos_posF_3= three_prime_cov_F %>% filter(strand=="+") %>% group_by(pos) %>% summarise(sum_pos=sum(count)) 
cov_bypos_negF_3= three_prime_cov_F %>% filter(strand=="-") %>% group_by(pos) %>% summarise(sum_pos=sum(count))
cov_bypos_neg_vecF_3= rev(as.numeric(unlist(cov_bypos_negF_3[,2])))

cov_byposF_3=cbind(cov_bypos_posF_3, cov_bypos_neg_vecF_3)

cov_bypos_allF_3= cov_byposF_3 %>% mutate(sum_by_pos=sum_pos + cov_bypos_neg_vec2_3 )
cov_bypos_allF_3= cov_bypos_allF_3 %>% select(pos, sum_by_pos)
```

```{r}
cov_bypos_all_longF_3=melt(cov_bypos_allF_3, id.vars = 'pos', value.name ='count' ) 

ggplot(cov_bypos_all_longF_3,aes(pos,count)) + geom_line() + ggtitle("3' splice site filtered exons") 

```

####Change data structure 

I want the data to be in a matrix exon by position. The row name is the every 80th entry of of the coverage file (1, 81, 161) and there should be 1906 rows. The rows are the 80 counts in the count column of the coverage file. I need to make a for loop through the rows that goes through seq(1,152480,80). I run this on cov_bypos_pos2_small first. 


```{r}
#five_prime_cov2_small=five_prime_cov2[1:160,]
#update data upload to have string at factor =false 
make_matrix=function(cov_df){
  matrix2=c(1:80)
  names2=vector()
for (i in seq(1,nrow(cov_df),80)){
  names2= append(names2,cov_df[i,4])
  row_i=vector()
  for (ea in seq(0,79,1)){
    row_i= append(row_i, cov_df[i + ea,8])
  }
  matrix2=rbind(matrix2, row_i)
}
  return(as.matrix(matrix2[2:nrow(matrix2),]))
  
}
```

Try this on the five prime coverage2 file. I need to normalize the points in the matrix so some are not super high.
```{r}
five_prime_matrix2=make_matrix(five_prime_cov2)
five_prime_matrix2_norm=apply(t(five_prime_matrix2), 1, rescale)

```






Make an image picture:  

```{r}
my_palette <- colorRampPalette(c("black", "white"))(n = 10)
image(five_prime_matrix2_norm,col=my_palette, ylab="exon", xlab="Position")

```

Maybe this is not the normalization I want. I should try binary. If there is a read make it 1.









####Filter out first and last exon 
This may help us understand the wierd 














####Extra code/false attempts
Now make a python script that takes this and the genome coverage file in as a data frame. I will then make a list of the base counts corresponding to each exon region from the genome coverage file. Do it for the 5 prime file first.  

```{python, eval=FALSE}
import pandas as pd

exon_5prime= pd.read_table("/project2/gilad/briana/Net-seq-pilot/data/exon_cov/top5_exonlist_18486_fiveprime_noCHR.txt", header=None)

gen_cov= pd.read_table("/project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-18486_combined_Netpilot-sort.cov.bed", header=None)

#will make a list of lists that I will turn into a matrix later  
exon_list=[]

for exon in exon_5prime.iterrows():
  chr=exon[1]
  start=exon[2]
  end=exon[3]
  
  


```


Test on exon_5prime=pd.read_table("/project2/gilad/briana/Net-seq-pilot/data/exon_cov/exon_5test.txt", header=None)  


```{bash, eval=FALSE}
awk 'BEGIN {ORS=","}; $1==1 && $2>=11968288 && $2<=11968368 {print $3}; END {print "\n"}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-18486_combined_Netpilot-sort.cov.bed 
```




## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
