---
title: "SMASH_smooth"
author: "Briana Mittleman"
date: "7/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Use SMASH to smooth regions of the Netseq data.  

I want to use the first 8 lines (NET3)  
  
* 18505  

* 18508  

* 18486  

* 19239  

* 19141  

* 19193  

* 19257  

* 19128 

The coverage files I need to make the matrix are in /project2/gilad/briana/Net-seq-pilot/data/cov. 

##ACTB
I am going to look at the region chr7:5,565,291-5,573,483 around the actb gene.  


```{bash, eval=F}
#!/bin/bash

#SBATCH --job-name=testsmash.actb
#SBATCH --account=pi-yangili1
#SBATCH --time=24:00:00
#SBATCH --output=testsmash.actb.out
#SBATCH --error=testsmash.actb.err
#SBATCH --partition=broadwl
#SBATCH --mem=20G
#SBATCH --mail-type=END

awk '$1 == 7 && $2 >= 5565291 && $2 <= 5573483 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-18486_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-18486_combined_Netpilot-actb.bed



awk '$1 == 7 && $2 >= 5565291 && $2 <= 5573483 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-18505_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-18505_combined_Netpilot-actb.bed

awk '$1 == 7 && $2 >= 5565291 && $2 <= 5573483 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-18508_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-18508_combined_Netpilot-actb.bed



awk '$1 == 7 && $2 >= 5565291 && $2 <= 5573483 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19128_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19128_combined_Netpilot-sort.actb.bed


awk '$1 == 7 && $2 >= 5565291 && $2 <= 5573483 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19141_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19141_combined_Netpilot.actb.bed


awk '$1 == 7 && $2 >= 5565291 && $2 <= 5573483 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19193_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19193_combined_Netpilot.actb.bed


awk '$1 == 7 && $2 >= 5565291 && $2 <= 5573483 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19239_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19239_combined_Netpilot.actb.bed


awk '$1 == 7 && $2 >= 5565291 && $2 <= 5573483 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19257_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19257_combined_Netpilot.actb.bed
```



Load Packages:
```{r}
library(devtools)
library(scales)
library(smashr)
library(tidyr)
library(workflowr)
library(dplyr)
```


```{r}
actb_18486=read.table("../data/smash_test/YG-SP-NET3-18486_combined_Netpilot-actb.bed", col.names=c("chr", "base", "net18486"))

actb_18505=read.table("../data/smash_test/YG-SP-NET3-18505_combined_Netpilot-actb.bed", col.names=c("chr", "base", "net18505"))

actb_18508=read.table("../data/smash_test/YG-SP-NET3-18508_combined_Netpilot-actb.bed", col.names=c("chr", "base", "net18508"))

actb_19128=read.table("../data/smash_test/YG-SP-NET3-19128_combined_Netpilot.actb.bed", col.names=c("chr", "base", "net19128"))

actb_19141=read.table("../data/smash_test/YG-SP-NET3-19141_combined_Netpilot.actb.bed", col.names=c("chr", "base", "net19141"))

actb_19193=read.table("../data/smash_test/YG-SP-NET3-19193_combined_Netpilot.actb.bed", col.names=c("chr", "base", "net19193"))

actb_19239=read.table("../data/smash_test/YG-SP-NET3-19239_combined_Netpilot.actb.bed", col.names=c("chr", "base", "net19239"))

actb_19257=read.table("../data/smash_test/YG-SP-NET3-19257_combined_Netpilot.actb.bed", col.names=c("chr", "base", "net19257"))
```

Make matrix
```{r}
actb_matrix=cbind(actb_18486$net18486, actb_18505$net18505,actb_18508$net18508, actb_19128$net19128, actb_19141$net19141,actb_19193$net19193, actb_19239$net19239, actb_19257$net19257) %>%t
```

write the matrix out:  

```{r}
#write.table(actb_matrix, "../data/smash_test/actb_countmatrix.txt", quote = F, row.names = F, col.names = F)
```


Run smash:  

```{r}
actb_res = smash.poiss(actb_matrix[1,]+actb_matrix[2,]+ actb_matrix[3,]+ actb_matrix[4,]+actb_matrix[5,]+actb_matrix[6,]+actb_matrix[7,]+actb_matrix[8,], post.var=TRUE)
```



```{r}

region=5565291:5573483


plot(region,actb_res$est,type='l',xlab="position",ylab="intensity", main="SMASH results ACTB")

```

Next I want to run it seperatly for all 8 individuals and plot them together to see if the peaks line up.  

```{r}
actb_res1 = smash.poiss(actb_matrix[1,], post.var=TRUE)

actb_res2 = smash.poiss(actb_matrix[2,], post.var=TRUE)

actb_res3 = smash.poiss(actb_matrix[3,], post.var=TRUE)

actb_res4 = smash.poiss(actb_matrix[4,], post.var=TRUE)

actb_res5 = smash.poiss(actb_matrix[5,], post.var=TRUE)

actb_res6 = smash.poiss(actb_matrix[6,], post.var=TRUE)

actb_res7 = smash.poiss(actb_matrix[7,], post.var=TRUE)

actb_res8 = smash.poiss(actb_matrix[8,], post.var=TRUE)

```
Make results matrix:  

```{r}
res_matrix=rbind(actb_res$est,actb_res1$est,actb_res2$est,actb_res3$est,actb_res4$est,actb_res5$est,actb_res6$est,actb_res7$est,actb_res8$est)

#write.table(res_matrix, "../data/smash_test/actb_smash_res.txt", quote = F, col.names = F, row.names = F, sep="\t")
```


```{r}

par(mfrow=c(3,3))
plot(region,actb_res$est,type='l',xlab="position",ylab="intensity", main="Combined")
plot(region,actb_res1$est,type='l',xlab="position",ylab="intensity", main="18486")
plot(region,actb_res2$est,type='l',xlab="position",ylab="intensity",main="18505")
plot(region,actb_res3$est,type='l',xlab="position",ylab="intensity",main="18508")
plot(region,actb_res4$est,type='l',xlab="position",ylab="intensity",main="19128")
plot(region,actb_res5$est,type='l',xlab="position",ylab="intensity",main="19141")
plot(region,actb_res6$est,type='l',xlab="position",ylab="intensity",main="19193")
plot(region,actb_res7$est,type='l',xlab="position",ylab="intensity",main="19239")
plot(region,actb_res8$est,type='l',xlab="position",ylab="intensity",main="19257")

```



I also am going to run it on the Mayer hek data.  

```{bash, eval=F}
#!/bin/bash

#SBATCH --job-name=testsmash.actb
#SBATCH --account=pi-yangili1
#SBATCH --time=24:00:00
#SBATCH --output=testsmash.actb.out
#SBATCH --error=testsmash.actb.err
#SBATCH --partition=broadwl
#SBATCH --mem=20G
#SBATCH --mail-type=END


awk '$1 == 7 && $2 >= 5565291 && $2 <= 5573483 {print}' /project2/gilad/briana/mayer.data/mayer_hek/data/cov/mayer_hek-sort.dedup.cov.bed > /project2/gilad/briana/mayer.data/mayer_hek/data/mayer_hek-dedup-smashactb.bed
```
This is not the correct coverage file to run this on. I need to make a genome coverage file of the data then I can run this.  

##COMT

Second gene to look at COMT chr22:19,928,209-19,960,444



```{bash, eval=F}
#!/bin/bash

#SBATCH --job-name=testsmash.comt
#SBATCH --account=pi-yangili1
#SBATCH --time=24:00:00
#SBATCH --output=testsmash.comt.out
#SBATCH --error=testsmash.comt.err
#SBATCH --partition=broadwl
#SBATCH --mem=20G
#SBATCH --mail-type=END

awk '$1 == 22 && $2 >= 19928209 && $2 <= 19960444 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-18486_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-18486_combined_Netpilot.comt.bed


awk '$1 == 22 && $2 >= 19928209 && $2 <= 19960444 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-18505_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-18505_combined_Netpilot.comt.bed

awk '$1 == 22 && $2 >= 19928209 && $2 <= 19960444 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-18508_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-18508_combined_Netpilot.comt.bed



awk '$1 == 22 && $2 >= 19928209 && $2 <= 19960444 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19128_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19128_combined_Netpilot.comt.bed


awk '$1 == 22 && $2 >= 19928209 && $2 <= 19960444 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19141_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19141_combined_Netpilot.comt.bed


awk '$1 == 22 && $2 >= 19928209 && $2 <= 19960444 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19193_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19193_combined_Netpilot.comt.bed


awk '$1 == 22 && $2 >= 19928209 && $2 <= 19960444 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19239_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19239_combined_Netpilot.comt.bed


awk '$1 == 22 && $2 >= 19928209 && $2 <= 19960444 {print}' /project2/gilad/briana/Net-seq-pilot/data/cov/YG-SP-NET3-19257_combined_Netpilot-sort.cov.bed > /project2/gilad/briana/Net-seq-pilot/data/smash.test/YG-SP-NET3-19257_combined_Netpilot.comt.bed

```



```{r}
comt_18486=read.table("../data/smash_test/YG-SP-NET3-18486_combined_Netpilot-comt.bed", col.names=c("chr", "base", "net18486"))

comt_18505=read.table("../data/smash_test/YG-SP-NET3-18505_combined_Netpilot-comt.bed", col.names=c("chr", "base", "net18505"))

comt_18508=read.table("../data/smash_test/YG-SP-NET3-18508_combined_Netpilot-comt.bed", col.names=c("chr", "base", "net18508"))

comt_19128=read.table("../data/smash_test/YG-SP-NET3-19128_combined_Netpilot-comt.bed", col.names=c("chr", "base", "net19128"))

comt_19141=read.table("../data/smash_test/YG-SP-NET3-19141_combined_Netpilot.comt.bed", col.names=c("chr", "base", "net19141"))

comt_19193=read.table("../data/smash_test/YG-SP-NET3-19193_combined_Netpilot-comt.bed", col.names=c("chr", "base", "net19193"))

comt_19239=read.table("../data/smash_test/YG-SP-NET3-19239_combined_Netpilot.comt.bed", col.names=c("chr", "base", "net19239"))

comt_19257=read.table("../data/smash_test/YG-SP-NET3-19257_combined_Netpilot.comt.bed", col.names=c("chr", "base", "net19257"))

```

Make matrix
```{r}
comt_matrix=cbind(comt_18486$net18486, comt_18505$net18505,comt_18508$net18508, comt_19128$net19128, comt_19141$net19141,comt_19193$net19193, comt_19239$net19239, comt_19257$net19257) %>%t
```

write the matrix out:  

```{r}
#write.table(comt_matrix, "../data/smash_test/comt_countmatrix.txt", quote = F, row.names = F, col.names = F)
```


Run smash:  

```{r}
comt_res = smash.poiss(comt_matrix[1,]+comt_matrix[2,]+ comt_matrix[3,]+ comt_matrix[4,]+comt_matrix[5,]+comt_matrix[6,]+comt_matrix[7,]+comt_matrix[8,], post.var=TRUE)

comt_res1 = smash.poiss(comt_matrix[1,], post.var=TRUE)

comt_res2 = smash.poiss(comt_matrix[2,], post.var=TRUE)

comt_res3 = smash.poiss(comt_matrix[3,], post.var=TRUE)

comt_res4 = smash.poiss(comt_matrix[4,], post.var=TRUE)

comt_res5 = smash.poiss(comt_matrix[5,], post.var=TRUE)

comt_res6 = smash.poiss(comt_matrix[6,], post.var=TRUE)

comt_res7 = smash.poiss(comt_matrix[7,], post.var=TRUE)

comt_res8 = smash.poiss(comt_matrix[8,], post.var=TRUE)

```


Make results matrix:  

```{r}
res_matrix_comt=rbind(comt_res$est,comt_res1$est,comt_res2$est,comt_res3$est,comt_res4$est,comt_res5$est,comt_res6$est,comt_res7$est,comt_res8$est)

#write.table(res_matrix_comt, "../data/smash_test/comt_smash_res.txt", quote = F, col.names = F, row.names = F, sep="\t")
```


```{r}
comtregion=19928209:19960444

par(mfrow=c(3,3))
plot(comtregion,comt_res$est,type='l',xlab="position",ylab="intensity", main="Combined")
plot(comtregion,comt_res1$est,type='l',xlab="position",ylab="intensity", main="18486")
plot(comtregion,comt_res2$est,type='l',xlab="position",ylab="intensity",main="18505")
plot(comtregion,comt_res3$est,type='l',xlab="position",ylab="intensity",main="18508")
plot(comtregion,comt_res4$est,type='l',xlab="position",ylab="intensity",main="19128")
plot(comtregion,comt_res5$est,type='l',xlab="position",ylab="intensity",main="19141")
plot(comtregion,comt_res6$est,type='l',xlab="position",ylab="intensity",main="19193")
plot(comtregion,comt_res7$est,type='l',xlab="position",ylab="intensity",main="19239")
plot(comtregion,comt_res8$est,type='l',xlab="position",ylab="intensity",main="19257")

```


I will next subset the bam files for each of these regions to create bigwig files that can be uploaded to UCSC.  
```{bash, eval=F}
#!/bin/bash

#SBATCH --job-name=subset.actb
#SBATCH --account=pi-yangili1
#SBATCH --time=24:00:00
#SBATCH --output=subset.actb.out
#SBATCH --error=subset.actb.err
#SBATCH --partition=broadwl
#SBATCH --mem=20G
#SBATCH --mail-type=END

module load Anaconda3

source activate net-seq  


samtools view -bh /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET3-18486_combined_Netpilot-sort.bam 7:5565291-5573483 >  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-18486_combined_Netpilot.actb.bam


samtools view -bh /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET3-18505_combined_Netpilot-sort.bam 7:5565291-5573483 >  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-18505_combined_Netpilot.actb.bam


samtools view -bh /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET3-18508_combined_Netpilot-sort.bam 7:5565291-5573483 >  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-18508_combined_Netpilot.actb.bam


samtools view -bh /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET3-19128_combined_Netpilot-sort.bam 7:5565291-5573483 >  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19128_combined_Netpilot.actb.bam



samtools view -bh /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET3-19141_combined_Netpilot-sort.bam 7:5565291-5573483 >  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19141_combined_Netpilot.actb.bam


samtools view -bh /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET3-19193_combined_Netpilot-sort.bam 7:5565291-5573483 >  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19193_combined_Netpilot.actb.bam




samtools view -bh /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET3-19239_combined_Netpilot-sort.bam 7:5565291-5573483 >  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19239_combined_Netpilot.actb.bam



samtools view -bh /project2/gilad/briana/Net-seq-pilot/data/sort/YG-SP-NET3-19257_combined_Netpilot-sort.bam 7:5565291-5573483 >  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19257_combined_Netpilot.actb.bam



```


Make Bigwig using deepools command:    

```{bash, eval=FALSE}
#!/bin/bash


#SBATCH --job-name=actb_bigwig 
#SBATCH --time=8:00:00
#SBATCH --account=pi-yangili1
#SBATCH --time=24:00:00
#SBATCH --output=actb_bigwig.out
#SBATCH --error=act_bigmost.err
#SBATCH --partition=broadwl
#SBATCH --mem=20G
#SBATCH --mail-type=END

module load Anaconda3  

source activate net-seq  


bamCoverage -b  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-18486_combined_Netpilot.actb.bam -o /project2/gilad/briana/Net-seq-pilot/data/bigwig/YG-SP-NET3-18486_combined_Netpilot.actb.bw

bamCoverage -b  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-18505_combined_Netpilot.actb.bam -o /project2/gilad/briana/Net-seq-pilot/data/bigwig/YG-SP-NET3-18505_combined_Netpilot.actb.bw

bamCoverage -b  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-18508_combined_Netpilot.actb.bam -o /project2/gilad/briana/Net-seq-pilot/data/bigwig/YG-SP-NET3-18508_combined_Netpilot.actb.bw

bamCoverage -b  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19128_combined_Netpilot.actb.bam -o /project2/gilad/briana/Net-seq-pilot/data/bigwig/YG-SP-NET3-19128_combined_Netpilot.actb.bw

bamCoverage -b  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19141_combined_Netpilot.actb.bam -o /project2/gilad/briana/Net-seq-pilot/data/bigwig/YG-SP-NET3-19141_combined_Netpilot.actb.bw

bamCoverage -b  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19193_combined_Netpilot.actb.bam -o /project2/gilad/briana/Net-seq-pilot/data/bigwig/YG-SP-NET3-19193_combined_Netpilot.actb.bw

bamCoverage -b  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19239_combined_Netpilot.actb.bam -o /project2/gilad/briana/Net-seq-pilot/data/bigwig/YG-SP-NET3-19239_combined_Netpilot.actb.bw

bamCoverage -b  /project2/gilad/briana/Net-seq-pilot/data/subset_bam/YG-SP-NET3-19257_combined_Netpilot.actb.bam -o /project2/gilad/briana/Net-seq-pilot/data/bigwig/YG-SP-NET3-19257_combined_Netpilot.actb.bw
```


I also did this for the mayer_hek line.  


##Upload to UCSC  

Use the instrutions on https://rcc.uchicago.edu/docs/data-transfer/index.html#http-web-access to create a public directory and copy the files to my ~/public_html directory.  


'''
http://users.rcc.uchicago.edu/~brimittleman/mayer_hek.actb.bw 

http://users.rcc.uchicago.edu/~brimittleman/YG-SP-NET3-19257_combined_Netpilot.actb.bw

http://users.rcc.uchicago.edu/~brimittleman/YG-SP-NET3-19239_combined_Netpilot.actb.bw

http://users.rcc.uchicago.edu/~brimittleman/YG-SP-NET3-19193_combined_Netpilot.actb.bw

http://users.rcc.uchicago.edu/~brimittleman/YG-SP-NET3-19141_combined_Netpilot.actb.bw

http://users.rcc.uchicago.edu/~brimittleman/YG-SP-NET3-18486_combined_Netpilot.actb.bw

http://users.rcc.uchicago.edu/~brimittleman/YG-SP-NET3-18505_combined_Netpilot.actb.bw

http://users.rcc.uchicago.edu/~brimittleman/YG-SP-NET3-18508_combined_Netpilot.actb.bw

http://users.rcc.uchicago.edu/~brimittleman/YG-SP-NET3-19128_combined_Netpilot.actb.bw

'''
