---
title: "Strand Specificity of Net seq data"
author: "Briana Mittleman"
date: 2018-03-22
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

The purpose of this analysis is to explore the strand specificity of my net seq data. Within genes we expect strand specific expression and at TSS we would expect some convergent transcription. I  will filter the overlaping genes as done in the Meyer paper.  

Mayer filtering: Pol-II-transcribed genes that do not overlap other genes within 2.5 kb of the TSS and polyadenylation site and are longer than 2 kb


###Filter the genes  

bedtools closest -N  


Get the protein coding genes:  
```{bash, eval=FALSE}
grep 'protein_coding' gencode.v19.annotation.bed  | awk '$8 == "gene"' |cut -f1-6  |sed 's/^chr//' >  gencode.v19.annotation.proteincodinggene.bed 
```

Only keep genes that are 2kb. I want genes where end (3) - start (2) is greater than 2000

```{bash, eval=FALSE }
awk '{if( ($3 - $2) > 2000)  print($1 "\t" $2 "\t" $3 "\t" $4 "\t" $5 "\t" $6)}' gencode.v19.annotation.proteincodinggene.bed > gencode.v19.annotation.proteincodinggene.2kb.bed
```

 
Next step is to look for overlab distance with bedtools closest -N.  

gene_dist.sh  

```{bash, eval=FALSE}

#!/bin/bash

#SBATCH --job-name=gene_dist
#SBATCH --time=8:00:00
#SBATCH --output=gene_dist.out
#SBATCH --error=gene_dist.err
#SBATCH --partition=gilad
#SBATCH --mem=10G
#SBATCH --mail-type=END

module load Anaconda3  

source activate net-seq 

bedtools closest -N -d -a /project2/gilad/briana/genome_anotation_data/gencode.v19.annotation.proteincodinggene.2kb.bed -b /project2/gilad/briana/genome_anotation_data/gencode.v19.annotation.proteincodinggene.2kb.bed > /project2/gilad/briana/genome_anotation_data/gencode.v19.annotation.proteincodinggene.2kb.dist.bed
```

Column 13 of this file must be > 2500  

```{bash, eval=FALSE}
awk '{if( $13 > 2500)  print($1 "\t" $2 "\t" $3 "\t" $4 "\t" $5 "\t" $6)}' gencode.v19.annotation.proteincodinggene.2kb.dist.bed > gencode.v19.annotation.distfilteredgenes.bed
```
This leaves 9367 genes. 


###Get strand specific gene counts for these genes 


Do this for 18486 first.  

Sort both files with sort -k1,1 -k2,2n  

```{bash, eval=FALSE}

#!/bin/bash

#SBATCH --job-name=strand
#SBATCH --time=8:00:00
#SBATCH --output=strand.out
#SBATCH --error=strnad.err
#SBATCH --partition=broadwl
#SBATCH --mem=40G
#SBATCH --mail-type=END



bedtools coverage -counts -s -sorted -a /project2/gilad/briana/genome_anotation_data/gencode.v19.annotation.distfilteredgenes.sort.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-bedsort.bed  > /project2/gilad/briana/Net-seq-pilot/output/strand_spec/same_strand_genecounts_18486.txt 


bedtools coverage -counts -S -sorted -a /project2/gilad/briana/genome_anotation_data/gencode.v19.annotation.distfilteredgenes.sort.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-bedsort.bed  > /project2/gilad/briana/Net-seq-pilot/output/strand_spec/opp_strand_genecounts_18486.txt 
```


###Process data  

Library input:  

```{r}
library(dplyr)
library(workflowr)
library(ggplot2)
```


Input data:  
```{r}
opp_strand=read.table("../data/same_strand_genecounts_18486.txt", header=FALSE, stringsAsFactors = FALSE)
colnames(opp_strand)= c("chr", "start", "end", "gene","score", "strand", "opp_count")
same_strand=read.table("../data/opp_strand_genecounts_18486.txt", header=FALSE, stringsAsFactors = FALSE)
colnames(same_strand)= c("chr", "start", "end", "gene","score", "strand", "same_count")
```

Merge on the gene names:  

```{r}
full_strand=inner_join(same_strand,opp_strand, by=c(c("chr", "start", "end", "gene","score", "strand")))
full_strand= full_strand %>% mutate(perc_same=(same_count /(same_count + opp_count))) %>% filter(perc_same != "NaN")
```

###Explore data:  

```{r}
summary(full_strand$perc_same)
plot(sort(full_strand$perc_same, decreasing=TRUE), col=ifelse((sort(full_strand$perc_same, decreasing=TRUE)) >.5, "red", "black"), ylab="same strand / gene count", xlab="Genes ordered by strand spec percent", main="Gene counts strand specificity 18486")
legend("topright", legend = c("top 75%"), col=c("red"), pch=16, cex=1)
```
```{r}
boxplot(log10(full_strand$same_count), log10(full_strand$opp_count), names=c("Same strand", "Opposite Strand"), ylab="log10 Gene counts", main="Gene counts by strand")



```

I am going to run the gene counts analysis not strand specific to make sure I am getting a sum of the these counts.  
```{bash, eval=FALSE}

#!/bin/bash

#SBATCH --job-name=all_counts
#SBATCH --time=8:00:00
#SBATCH --output=all_strand.out
#SBATCH --error=all_strnad.err
#SBATCH --partition=broadwl
#SBATCH --mem=40G
#SBATCH --mail-type=END



bedtools coverage -counts  -sorted -a /project2/gilad/briana/genome_anotation_data/gencode.v19.annotation.distfilteredgenes.sort.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18486_combined_Netpilot-bedsort.bed  > /project2/gilad/briana/Net-seq-pilot/output/strand_spec/all_strand_genecounts_18486.txt 

```
This file confirmed that the counts without specificity is the sum of the strand information. 

###Try this analysis in another line  
strand_spec_18505.sh 

```{bash, eval=FALSE}
#!/bin/bash

#SBATCH --job-name=strand_18505
#SBATCH --time=8:00:00
#SBATCH --output=strand.out
#SBATCH --error=strnad.err
#SBATCH --partition=broadwl
#SBATCH --mem=40G
#SBATCH --mail-type=END


bedtools coverage -counts -s -sorted -a /project2/gilad/briana/genome_anotation_data/gencode.v19.annotation.distfilteredgenes.sort.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18505_combined_Netpilot-bedsort.bed  > /project2/gilad/briana/Net-seq-pilot/output/strand_spec/same_strand_genecounts_18505.txt 


bedtools coverage -counts -S -sorted -a /project2/gilad/briana/genome_anotation_data/gencode.v19.annotation.distfilteredgenes.sort.bed -b /project2/gilad/briana/Net-seq-pilot/data/bed/YG-SP-NET3-18505_combined_Netpilot-bedsort.bed  > /project2/gilad/briana/Net-seq-pilot/output/strand_spec/opp_strand_genecounts_18505.txt 
```

```{r}
opp_strand_18505=read.table("../data/same_strand_genecounts_18505.txt", header=FALSE, stringsAsFactors = FALSE)
colnames(opp_strand_18505)= c("chr", "start", "end", "gene","score", "strand", "opp_count")
same_strand_18505=read.table("../data/opp_strand_genecounts_18505.txt", header=FALSE, stringsAsFactors = FALSE)
colnames(same_strand_18505)= c("chr", "start", "end", "gene","score", "strand", "same_count")


full_strand_18505=inner_join(same_strand_18505,opp_strand_18505, by=c(c("chr", "start", "end", "gene","score", "strand")))
full_strand_18505= full_strand_18505 %>% mutate(perc_same=(same_count /(same_count + opp_count))) %>% filter(perc_same != "NaN")

summary(full_strand_18505$perc_same)
plot(sort(full_strand_18505$perc_same, decreasing = TRUE), col=ifelse((sort(full_strand_18505$perc_same, decreasing = TRUE))>.45, "red", "black"), ylab="same strand / gene count", xlab="Genes ordered by strand spec percent", main="Gene counts strand specificity 18505")
legend("topright", legend = c("top 75%"), col=c("red"), pch=16, cex=1)

```

```{r}
boxplot(log10(full_strand_18505$same_count), log10(full_strand_18505$opp_count), names=c("Same strand", "Opposite Strand"), ylab="log10 Gene counts", main="Gene counts by strand 18505")


```

###Distribution for genes >1 18486  


```{r}
gene_counts_18486=read.table("../data/all_strand_genecounts_18486.txt", stringsAsFactors = FALSE, header=FALSE)
colnames(gene_counts_18486)= c("chr", "start", "end", "gene","score", "strand", "count")
mapped_18486_mil= 65189389 / 10^6
gene_counts_18486=gene_counts_18486 %>% mutate(K_length= (end - start)/100) %>% mutate(rpkm= + count/(K_length * mapped_18486_mil)) %>% filter(rpkm>=1)

```
Join this with the strand specific information.  


```{r}
top_genes_strand= inner_join(full_strand, gene_counts_18486, by=c("chr", "start", "end", "gene","score", "strand"))
```

Plot this distribution:  
```{r}
plot(sort(top_genes_strand$perc_same, decreasing = TRUE), ylab="same strand / gene count", xlab="Genes ordered by strand spec percent", main="Gene counts strand specificity 18486 for genes >1 RPKM")
```

Box plots:  


```{r}
boxplot(log10(top_genes_strand$same_count), log10(top_genes_strand$opp_count), names=c("Same strand", "Opposite Strand"), ylab="log10 Gene counts", main="Gene counts by strand, genes >1 RPKM")

```



## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
