---
title: "Update Snakefile for pilot analysis"
author: "Briana Mittleman"
date: 2018-03-02
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

##Pilot data:  

The pilot project has 16 human lines of net-seq data. I have 3 lanes of sequencing for each library of 8. The first library is the same 8 samples from Net3. I can use zcat to combine the samles from seperate lanes into one file. I will call these [sample_name]_combined_Netpilot.fastq. I will use the project directory /project2/gilad/briana/Net-seq-pilot 

##Snakefile Update:  

I will update my snakefile by copying the old one as Snakefile_old.  

Changes:  

* change genome location to /project2/gilad/briana/genome_anotation_data  

* Add picard tools annotation to the snakefile  

* compute genome coverage for the dedup and sorted bam files  



###Genome location  

My old snakefile create the reference genome for every new analysis. It would be better to build the reference once and always keep it in one place. I will now be in /project2/gilad/briana/genome_anotation_data. To do this I will change the snakefile to point to this location and change the config file to point to the correct location.  
```{bash, eval=FALSE}
#config file  

dir_genome: /project2/gilad/briana/genome_anotation_data/

#snakefile
dir_gen=config["dir_genome"]
dir_genome= dir_gen + "genome/" 


```

###Picard tools  

Picard tools will take in a flat file and a rRna file and will assess coverage at genomic regions. Before I make the rule I need to convert the gencode.v19.annotation.gtf to a flat file.  

Update net-seq environment:  

* ucsc-gtfToGenePred  
* picard >= 2.9.2  

```{bash, eval=FALSE}
#convert gtf to genepred flat  
gtfToGenePred -genePredExt -ignoreGroupsWithoutExons gencode.v19.annotation.gtf gencode.v19.annotation.refFlat
```

Adapt rule from Seb's Snakefile  

```{bash, eval=FALSE}
#config file 
ref_flat: /project2/gilad/briana/genome_anotation_data/gencode.v19.annotation.refFlat
ribosome_intervals: /project2/gilad/briana/genome_anotation_data/hg19.rRNA.intervals  

#snakefile  
ref_flat = config["ref_flat"]
ribosome_int = config["ribosome_intervals"]


#rule 
rule collect_rna_metrics:
    input:
        bam = dir_sort + "{samples}-sort.bam"
        ref_flat = ref_flat,
        ribosome_int = ribosome_int
    output:
        rna_metrics = output + "{samples}_RNAmetrics.picard.txt"
    params:
        strand = "NONE",
        memory = "-Xmx12G"
    shell:
        "picard CollectRnaSeqMetrics {params.memory} I={input.bam} O={output.rna_metrics} REF_FLAT={input.ref_flat} STRAND={params.strand} RIBOSOMAL_INTERVALS={input.ribosome_int}"

```


###Genome Coverage  

The old snakefile has a genome_cov rule for genome cov of the deduplicated files. I want to do this for the sort and dedup files. I also will change the rule so it is -d -5.  
```{bash, eval=FALSE}
rule genome_cov_dedup:
    input:
       bamdedup = dir_dedup + "{samples}-sort.dedup.bam",
       genome = dir_genome + ensembl_genome + ".reads"
    output:
       dir_cov + "{samples}-sort.dedup.cov.bed"
    shell: "bedtools genomecov -d -5 -ibam {input.bamdedup} -g {input.genome} > {output}"
    
    
rule genome_cov_sort:
    input:
      bamsort = dir_sort + "{samples}-sort.bam"
      genome = dir_genome + ensembl_genome + ".reads"  
    output: 
      dir_cov + "{samples}-sort.cov.bed"
    shell: "bedtools genomecov -d -5 -ibam {input.bamsort} -g {input.genome} > {output}"
   
   
#in rule all:  
expand(dir_cov + "{samples}-sort.dedup.cov.bed", samples=samples),
expand(dir_cov + "{samples}-sort.cov.bed", samples=samples),
```


## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
