---
title: "Explore coverage within 3` UTRs"
author: "Briana Mittleman"
date: 2018-01-29
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->
I have a file with the 3` UTRs and I want to extract coverage from the drop and dronc seq bam files that are in these UTR regions.

I will use:  


- bedtools coverage -d -a /project2/gilad/spott/dropBams/Day7_cardiomyocytes_drop_seq.bam -b /project2/gilad/briana/apa_sites/three_prime_utr.bed > drop7_cardio_3utr.txt


This is taking too much memory. I am going to convert bam to a bed file then sort it.  
 
```{bash, eval=FALSE}
bedtools bamtobed -i /project2/gilad/spott/dropBams/Day7_cardiomyocytes_drop_seq.bam > Day7_cardiomyocytes_drop_seq.bed  

sort -k1,1 -k2,2n Day7_cardiomyocytes_drop_seq.bed >  Day7_cardiomyocytes_drop_seq_sort.bed 
```



Do this for the UTR file as well.  

```{bash, eval=FALSE}
sort -k1,1 -k2,2n three_prime_utr.bed > three_prime_utr_sort.bed  
```


Now add the sorted to the coverage:  Update the drop7_cardio_3UTR_cov.sh script  


```{bash, eval=FALSE}
bedtools coverage -d -sorted  -a /project2/gilad/briana/apa_sites/Day7_cardiomyocytes_drop_seq_sort.bed  -b /project2/gilad/briana/apa_sites/three_prime_utr_sort.bed > drop7_cardio_3utr.txt
```

Do this for one of 3' seq lines too (LCL). The scipt is called lcl_3UTR_cov.sh.  


These files are not correct. They have coverage for a region rather than per base in each UTR. Try to switch a and b in the script. 

Now this seems correct. THe file has the UTR regions. A line for each base in the region in column 6 and the coverage at that base in column 7.  

* LCL_3utrAB.bed  

* drop7_cardio_3utrAB.bed  

I will continue this analysis on the Rstudio for midway because the coverage files are so big.  

###Change data structure: 

I am now using a python dictionary to create a file that has the UTRs as keys and the values as a list of the read count for that UTR. The script is /project2/gilad/briana/apa_sites/code/cov_per_UTR.py  


To run this I have to make a bash  script. I called it test.sh for now.

It has the bash heading, module load python, and the following line to call the pythn script.  


'python cov_per_UTR.py ../LCL_3utrAB.bed ../output/cov_at_UTRs_LCL.csv'


This takes too long to run. I will up the time and add a step that creates a file from the UTR list. This will help me know if the keys are created partway through the run. The new py script is cov_per_UTR2.py and takes 3 arguments, data, a UTR_names file and a full output file. The bash script to run this is /project2/gilad/briana/apa_sites/code/utr_py_lcl.sh. I updates this file for the drop7 coverage file as well. The bash script for this is /project2/gilad/briana/apa_sites/code/utr_py_drop7.sh.  



###Use the group by function:

First seperate the files by pos and neg strand UTR

```{bash, eval=FALSE}

awk '{if ($6 == "+") {print} }' drop7_cardio_3utrAB.bed > drop7_cardio_3utrAB.pos.bed
awk '{if ($6 == "-") {print} }' drop7_cardio_3utrAB.bed > drop7_cardio_3utrAB.neg.bed


awk '{if ($6 == "-") {print} }' LCL_3utrAB.bed > LCL_3utrAB.neg.bed
awk '{if ($6 == "+") {print} }' LCL_3utrAB.bed > LCL_3utrAB.pos.bed

```

Use the group by bedtools function to group by the 7th column (base number in the UTR) and get the mean for the coverage at that base.  This script is /project2/gilad/briana/apa_sites/groupby/per_base_mean.sh 

```{bash, eval=FALSE}
#!/bin/bash


#SBATCH --job-name=mean_UTR
#SBATCH --time=2:00:00
#SBATCH --partition=gilad
#SBATCH --mem=10G
#SBATCH --mail-type=END
#SBATCH --ntasks-per-node=2

module load Anaconda3
source activate net-seq


bedtools groupby -i drop7_cardio_3utrAB.pos.bed -g 7 -c 8 -o mean > drop7_cardio_pos_mean.bed


bedtools groupby -i drop7_cardio_3utrAB.neg.bed -g 7 -c 8 -o mean > drop7_cardio_neg_mean.bed


bedtools groupby -i LCL_3utrAB.pos.bed -g 7 -c 8 -o mean > LCL_pos_mean.bed

bedtools groupby -i LCL_3utrAB.neg.bed -g 7 -c 8 -o mean > LCL_neg_mean.bed
```



This doesnt work. I am going to subset the file and try this for 1 chromosome.  

* less drop7_cardio_3utrAB.pos.bed |head -n 10000 |sort -k7,7n |bedtools groupby -i stdin -g 7 -c 8 -o mean | head -n 10000

```{bash, eval=FALSE}
awk '{if ($1 == "chr21") {print} }' drop7_cardio_3utrAB.pos.bed > drop7_cardio_3utrAB.pos.chr21.bed
```


```{r}
drop7_3UTR_pos_chr21= read.table("../data/drop7_cardio_3utrAB.pos.chr21.bed", header=FALSE)

```

```{r}
library(dplyr)
group_by(drop7_3UTR_pos_chr21, V7) %>% summarise(sum=sum(V8)) -> UTR_21_cov


plot(UTR_21_cov$sum, ylab="sum expression", xlab="UTR base position", main="Chr 21 3' UTR coverage Dropseq day 7")
```
```{r}
utr_unique_pos= unique(drop7_3UTR_pos_chr21[,1:3])
summary(utr_unique_pos$V3-utr_unique_pos$V2)
```


```{r}
plot(UTR_21_cov$sum, ylab="sum expression", xlab="UTR base position", main="Chr 21 3' UTR coverage Dropseq day 7", xlim = c(0,1000))
```




Do this on the negative strand. 

```{r}
drop7_3UTR_neg_chr21= read.table("../data/drop7_cardio_3utrAB.neg.chr21.bed", header=FALSE)
group_by(drop7_3UTR_neg_chr21, V7) %>% summarise(sum=sum(V8)) -> UTR_21neg_cov


plot(UTR_21neg_cov$sum, ylab="sum expression", xlab="UTR base position", main="Chr 21 3' UTR coverage Dropseq day 7")
```

Average utr size: 


```{r}
utr_unique= unique(drop7_3UTR_neg_chr21[,1:3])
summary(utr_unique$V3-utr_unique$V2)
```
Subset plot wit this information:  

```{r}
plot(UTR_21neg_cov$sum, ylab="sum expression", xlab="UTR base position- negative strand", main="Chr 21 3' UTR coverage Dropseq day 7", xlim=c(0,1000))
```

With the 3` seq:


```{r}
LCL_3UTR_neg_chr20= read.table("../data/LCL_3utrAB.neg.chr20.bed", header=FALSE)
group_by(LCL_3UTR_neg_chr20, V7) %>% summarise(sum=sum(V8)) -> LCL_UTR_20_cov
plot(LCL_UTR_20_cov$sum, ylab="mean expression", xlab="UTR base position", main="Chr 20 3' UTR coverage LCL")
```

```{r}
utr_lclneg_unique= unique(LCL_3UTR_neg_chr20[,1:3])
summary(utr_lclneg_unique$V3-utr_lclneg_unique$V2)
```

Plot a little past the median:  

```{r}
plot(LCL_UTR_20_cov$sum, ylab="mean expression", xlab="UTR base position", main="Chr 20 3' UTR coverage LCL", xlim=c(0,200))
```









```{r}
LCL_3UTR_pos_chr1= read.table("../data/LCL_3utrAB_pos.chr1.bed", header=FALSE)
group_by(LCL_3UTR_pos_chr1, V7) %>% summarise(sum=sum(V8)) -> LCL_UTR_1_cov
plot(LCL_UTR_1_cov$sum, ylab="mean expression", xlab="UTR base position", main="Chr 1 3' UTR coverage LCL")

```


## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
